### 2020-03-18 text/manuscript.tex
PLOS template

% Template for PLoS
% Version 3.5 March 2018
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Which sectors are most prone to social distancing measures?} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Miklós Koren\textsuperscript{1,2,3\Yinyang\textcurrency*},
Rita Pető\textsuperscript{2\ddag}
\\
\bigskip
\textbf{1} Central European University, Budapest, Hungary
\\
\textbf{2} KRTK KTI, Budapest, Hungary
\\
\textbf{3} CEPR, London, UK
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
\Yinyang This author is responsible for the research idea, the theoretical model, the analysis of the spatial data and the first draft of the manuscript.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
\ddag This author is responsible for the analysis of the occupation data, reviewing and discussing results and editing the manuscript.

% Current address notes
\textcurrency Current Address: Central European University, Nádor u. 9., 1051 Budapest, Hungary % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address 
% \textcurrency c Insert third current address

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* korenm@ceu.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\linenumbers

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}
Social distancing measures are effective non-pharmaceutical interventions against the rapid spread of epidemics (REFs). Many countries have implemented or are considering measures such as school closures, prohibition of large gatherings and transportation to slow down the spread of the coronavirus (REFs). What are the economic effects of such social distancing interventions? Which are the firms and industries most affected by the restrictions?

Past research has analyzed the efficacy of social distancing interventions on reducing the spread of epidemics using the 1918 Spanish Flu in the US (REF) and seasonal viral infections in France (REF) [add more REFs]. Our knowledge of economic impacts, however, is limited. For this question, the case of the Spanish Flu pandemic is less relevant, as the importance of face-to-face communication has increased in the last 100 years through urbanization (REF) and XXX services (REF).

\section{A model of }

\section{Methodology}
We compute two measures of exposure to social distancing interventions. The first is the share of workers whose job requires personal communications. This is high for sectors like XX and low for sectors like XX. The idea is that when workers in communication-intensive occupations stay at home, their productivity decreases. A challenge to this assumption is that, in some occupations, online communication can partly substitute face-to-face communication.

The second measure captures how urbanized workers are: what fraction of them work in high population or employment density areas. This is high for sectors like XX and low for sectors like XX. When the demand for face-to-face communication, either within the firm or with consumers is large, firms are likely to agglomerate in large cities. The challenge to this measure is that agglomeration may also be driven by a minimization of transportation costs.

Taken together, high values of both measures of communication intensity and agglomeration coefficient can indicate that face-to-face communication (as opposed to online communication or transportation) is used intensively in the sector.

\section{Data}
ONET
CBP density
CBP plant size

## Cross walks
## Construction of communication index
## Worker density

Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\begin{eqnarray}
\label{eq:schemeP}
	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
\end{eqnarray}

\section*{Materials and methods}
\subsection*{Etiam eget sapien nibh}

% For figure citations, please use "Fig" instead of "Figure".
Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Place figure captions after the first paragraph in which they are cited.
\begin{figure}[!h]
\caption{{\bf Bold the figure title.}
Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}

% Results and Discussion can be combined.
\section*{Results}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Place tables after the first paragraph in which they are cited.
\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
\subsection*{\lorem\ and \ipsum\ nunc blandit a tortor}
\subsubsection*{3rd level heading} 
Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit. Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat.

\begin{enumerate}
	\item{react}
	\item{diffuse free particles}
	\item{increment time by dt and go to 1}
\end{enumerate}

\subsection*{Sed ac quam id nisi malesuada congue}

Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\begin{itemize}
	\item First bulleted item.
	\item Second bulleted item.
	\item Third bulleted item.
\end{itemize}

\section*{Discussion}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero~\cite{bib3}.

\section*{Conclusion}

CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.

Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor. For more information, see \nameref{S1_Appendix}.

\section*{Supporting information}

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 File.}
\label{S1_File}
{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Video.}
\label{S1_Video}
{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Appendix.}
\label{S1_Appendix}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Table.}
\label{S1_Table}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\section*{Acknowledgments}
Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.

\nolinenumbers

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for 
% step-by-step instructions.
% 
\begin{thebibliography}{10}

\bibitem{bib1}
Conant GC, Wolfe KH.
\newblock {{T}urning a hobby into a job: how duplicated genes find new
  functions}.
\newblock Nat Rev Genet. 2008 Dec;9(12):938--950.

\bibitem{bib2}
Ohno S.
\newblock Evolution by gene duplication.
\newblock London: George Alien \& Unwin Ltd. Berlin, Heidelberg and New York:
  Springer-Verlag.; 1970.

\bibitem{bib3}
Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
  infection through a transposon insertion followed by a {D}uplication}.
\newblock PLoS Genet. 2011 Oct;7(10):e1002337.

\end{thebibliography}

\end{document}

### 2020-03-18 text/manuscript.tex
First draft of model

@@
 
-\section{A model of }
+\section{A model of communication}
+
+Production involves sequentally completing tasks indexed by $z\in[0,1]$.
+A single worker can do a range of tasks, but there is benefit to specialization and division of labor (Adam Smith and Acemogul> REF).
+The labor cost of a worker completing $Z<1$ measure of tasks is $wZ^{1+\gamma}/\gamma$, where $w$ is the wage rate, and $\gamma>0$ captures the benefits to division of labor.
+As we show below, the higher the $\gamma$, the more specialized each worker will be in a narrower set of tasks.
+
+Once the range of tasks $Z$ is completed, the worker passes the unfinished product on to another worker.
+This has a cost $c$, which can capture the cost of communication either face-to-face or online.
+The determinants of communication cost will parametrized later.
+
+The firm will optimally decide how to share tasks between workers.
+The key trade-off is economizing on the cost of communication while exploiting the division of labor.
+Let $n$ denote the number of workers involved in the production process.
+Because workers are symmetric, each works on $Z=1/n$ range of tasks before passing the work to the next worker.
+The process involves $n-1$ ``contacts'' (instances of communication), which can be approximated by $n$ if $n$ is sufficiently large.
+
+The firm's cost minimization problem can then be written as a function of the number of contacts alone,
+\begin{equation}
+	\min_n nc + \frac w\gamma n^{-\gamma},
+\end{equation}
+where total communication costs are $nc$ and production costs are $w n Z^{1+\gamma}/\gamma$ with $Z=1/n$.
+
+Given the strict convexity of this cost function, the first-order condition is necessary and sufficient for the optimum,
+\begin{equation}
+	n^*(c) = (c/w)^{-1/(1+\gamma)}.
+\end{equation}
+The number of worker contacts is decreasing in the cost of communication, expressed relative to worker wage.
+When the division of labor is important, $\gamma$ is high, and the number of contacts does not depend very strongly on communication costs.
+
+The total cost of producing one good can be calculated by substituting in \eqref{} into \eqref{},
+\begin{equation}
+	\frac1\chi c^{\chi}w^{1-\chi},
+\end{equation}
+where $\chi=\gamma/(1+\gamma)\in(0,1)$ measures the importance of division of labor.
+This unit cost function is the same as if workers and communication were substitutable in the production function in a Cobb-Douglas fashion.
+Here $\chi$ captures the share of costs associated with communication.
+[NB: and could hence be calibrated to the share of non-production workers]
+\subsection{The cost of communication}
+Firms can chose between two ways of organizing communication.
+First, they can ask workers to meet face to face, in which case communication costs depends inversely on the population density in the neighborhood of the firm, $c=d^{-\tau}$.
+This captures the Marshallian externality of knowledge spillovers (REF), which happen more easily in densely populated areas.
+Second, they can ask workers to  interact with one another through telecommunication, in which case $c=T$.
+In sectors where telecommunication is not feasible, we can take $T$ to be prohibitively large.
+
+The firm will chose the cheaper of the two forms of communcation,
+\begin{equation}
+	c = \min \{d^{-\tau}, T\}.
+\end{equation}
+The unit cost of production can be calculated by substituting in \eqref{} into \eqref{},
+\begin{equation}
+\frac {w^{1-\chi}}{\chi}
+\min \{
+	d^{-\tau\chi},T^\chi
+\}.
+\end{equation}
+Because both wages and land rents are higher in places with high population density (REF), a firm will only move to such location when either the communication benefits $\tau\chi$ are high, or the cost of telecommunication $T$ is high.
+In spatial equilibrium (not modeled here), firms with high communication needs will choose to locate in high-density areas.
+
+\subsection{Social distancing measures}
+We study the effect of a of social distancing intervention that introduces an upper bound $N$ on the number of face-to-face contacts, but places no restriction on telecommunication.
+
+Take a firm that is using face-to-face communication, such that $d>T^{-1/\tau}$.
+(If the firm is already relying on telecommunication, they are unaffected by social distancing.) The optimal number of contacts without social distancing would be $n^* = d^{\tau(1-\chi)}w^{1-\chi}$.
+The firm is affected by the first type of social distancing if $n^*>N$, that is,
+\begin{equation}
+	d > N^{1/\tau(1-\chi)} w^{-1/\tau}.
+\end{equation}
+This is more likely to hold for firms in high-density areas (high $d$) and those with high division of labor ($\chi$ close to one).
+These are both contributors to a high number of face-to-face contacts.
+Density and the prevalence of communication are positive predictors to sensitivity to social distancing.
+
+How do these firms react to social distancing?
+They can limit face-to-face communication and decrease worker productivity (because each worker has to work on a wider range of tasks than they used to).
+[NB: cite digital education as an example in the introduction] Or they can mandate telecommuting and avoid face-to-face communication this way.
+The firm will chose the strategy that leads to the least increase in costs.
+They will switch to telecommuting if
+\begin{equation}
+	T < w N^{\chi-1}.
+\end{equation}
+Firms with low telecommunication costs $T$, high worker wages $w$ and low communication intensity $\chi$ are more likely to switch to telecommuting.
+Telecommuting is also more likely for more stringent social distancing measures (low $N$).
+Firms with high communication intensity are hurt the most by social distancing, because for them telecommuting is not a viable option.
+
+\subsection{Discussion}
 

### 2020-03-18 text/manuscript.tex
Add draft introduction

@@
 \section*{Abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
-Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-\section*{Author summary}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
-Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+Social distancing interventions can be effective against epidemics, but little is known about their economic effects.
+We develop a model of communication and production to study the effects of a policy that limits face-to-face interactions.
+This policy results in the highest cost increases in sectors with high division of labor and hence high need for communication and those that are located in urban centers with high population density.
+We measure the prevalence of communication-related tasks and the urban density of workers for each detailed industry in the U.S.
+We predict that XX, XX and XX will suffer the biggest employment losses in response to the 2019--20 coronavirus pandemic.
+Overall, XX people work in the most affected sectors.
 
@@
 
-Past research has analyzed the efficacy of social distancing interventions on reducing the spread of epidemics using the 1918 Spanish Flu in the US (REF) and seasonal viral infections in France (REF) [add more REFs].
+Past research has analyzed the efficacy of social distancing interventions on reducing the spread of epidemics using the 1918 Spanish Flu in the U.S.
+(REF) and seasonal viral infections in France (REF).
 Our knowledge of economic impacts, however, is limited.
-For this question, the case of the Spanish Flu pandemic is less relevant, as the importance of face-to-face communication has increased in the last 100 years through urbanization (REF) and XXX services (REF).
+For this question, the case of the Spanish Flu pandemic is less relevant, as the importance of face-to-face communication has increased in the last 100 years through urbanization (REF) and an increased specialization in business services (REF).
 
+We build a model of communication within the production process to understand how limiting face-to-face interaction increases costs.
+Without social distancing, workers specialize in a narrow range tasks and interact with other workers completing other tasks.
+This division of labor reduces production costs but requires frequent contact between workers.
+In the model, the number of contacts per worker are the most frequent in high population density areas in sectors where division of labor is important.
+When face-to-face interaction is limited, these are the locations and sectors that suffer the largest cost increases.
+Our model can also explain when telecommunication is a low-cost substitute for face-to-face interaction.
+
+To measure sensitivity to social distancing, we turn to recent data on the task descriptions of each occupation (REF) and the precise geographic location of non-farm businesses (REF).
+We classify workers as affected if their occupation requires frequent communication with others (inside or outside the firm).
+The most affected group of workers includes healthcare professionals, teachers, and managers.
+Sectors are affected if they employ most of their workers in high-density ZIP-code areas.
+The most affected sectors are apparel manufacturing, information and business services, and performing arts.
+Both measures are necessary to understand exposure to social distancing.
+Firms may also locate in urban centers to minimize shipping costs with respect to suppliers and customers.
+But if they also have a high prevalence of communication-related tasks, we conclude that they are heavily relying on face-to-face communication, and will be particularly hurt by social distancing.
+
+For completeness, we also compute, for each industry, the fraction of workers who work with many coworkers in enclosed space or subject to potential infections, or working in large plants.
+These additional measures are highly correlated with our two preferred indicators (CHECK).
+We report our four index of exposure to social distancing for each 5-digit occupation, each 3-digit NAICS industry, and each 5-digit ZIP-Code Tabulation Area.
+Industries that are in the top quartile of both  communication exposure and urban density altogether employ XX workers in the U.S.
 \section{A model of communication}
@@
 
-## Cross walks
-## Construction of communication index
-## Worker density
-
-Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
-
-\begin{eqnarray}
-\label{eq:schemeP}
-	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
-\end{eqnarray}
-
-\section*{Materials and methods}
-\subsection*{Etiam eget sapien nibh}
-
-% For figure citations, please use "Fig" instead of "Figure".
-Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
-
+Cross walks
+Construction of communication index
+Worker density
 % Place figure captions after the first paragraph in which they are cited.
@@
 \section*{Results}
-Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
 
@@
 \end{table}
-
-%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
-\subsection*{\lorem\ and \ipsum\ nunc blandit a tortor}
-\subsubsection*{3rd level heading} 
-Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
-Sed non aliquet felis.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet.
-Sed suscipit iaculis mi at feugiat.
-
-\begin{enumerate}
-	\item{react}
-	\item{diffuse free particles}
-	\item{increment time by dt and go to 1}
-\end{enumerate}
-
-\subsection*{Sed ac quam id nisi malesuada congue}
-
-Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
-
-\begin{itemize}
-	\item First bulleted item.
-	\item Second bulleted item.
-	\item Third bulleted item.
-\end{itemize}
 

### 2020-04-04 text/abstract.tex
Add text

Social distancing interventions can be effective against epidemics but are potentially detrimental for the economy.
Businesses that rely heavily on face-to-face communication or close physical proximity when producing a product or providing a service are particularly vulnerable. 
There is, however, no systematic evidence about the role of human interactions across different lines of business and about which will be the most limited by social distancing.
Here we provide theory-based measures of the reliance of U.S. businesses on human interaction, detailed by industry and geographic location.
We find that 49 million workers work in occupations that rely heavily on face-to-face communication or require close physical proximity to other workers. Our model suggests that when businesses are forced to reduce worker contacts by half, they need a 12 percent wage subsidy to compensate for the disruption in communication. Retail, hotels and restaurants, arts and entertainment and schools are the most affected sectors.
Our results can help target fiscal assistance to businesses that are most disrupted by social distancing.

### 2020-04-04 text/content.tex
Add text

\section*{Introduction}
Social distancing measures are effective non-pharmaceutical interventions against the rapid spread of epidemics \cite{Bootsma2007-ww,Markel2007-ad,Hatchett2007-gc,Wilder-Smith2020-jj}. Many countries have implemented or are considering measures such as school closures, prohibition of large gatherings and restrictions on non-essential stores and transportation to slow down the spread of the 2019--20 coronavirus pandemic \cite{Anderson2020-qk,Cohen2020-jw,Thompson2020-lc,noauthor_2020-xi}. What are the economic effects of such social distancing interventions? Which businesses are most affected by the restrictions?

Past research has analyzed the efficacy of social distancing interventions on reducing the spread of epidemics using the 1918 Spanish Flu in the U.S. \cite{Hatchett2007-gc,Markel2007-ad,Bootsma2007-ww} and seasonal viral infections in France \cite{Adda2016-mn}. Our knowledge of economic impacts, however, is limited \cite{Wren-Lewis2020-vc}. For this question, past data may be less relevant, as the importance of face-to-face communication has increased steadily in the last 100 years through urbanization \cite{Henderson2010-mv,Henderson2002-ji} and specialization increased in business services as well \cite{Herrendorf2014-jx,Duarte2019-kc}.

The starting point of this paper is the observation that many sectors rely heavily on face-to-face communication in the production process \cite{Charlot2004-zr,Tian2019-wq}. We build a model of communication to understand how limiting face-to-face interaction increases production costs. Without social distancing, workers specialize in a narrow range of tasks and interact with other workers completing other tasks. This division of labor reduces production costs but requires frequent contact between workers. In the model, the number of contacts per worker is the most frequent in high-population-density areas in businesses where the division of labor is important. When face-to-face interaction is limited, these are exactly the businesses that suffer the most.

To measure business disruptions from social distancing, we turn to recent data on the task descriptions of each occupation \cite{National_Center_for_ONET_Development2020-wj} and the precise geographic location of non-farm businesses in the U.S. \cite{CBP}. We construct three groups of occupations and study their distribution in space. First, some occupations require face-to-face communication several times a week with other workers. Examples of these \emph{teamwork-intensive} occupations include maintenance, personal care related occupations and health care professionals. Other occupations require frequent contact with customers. Counselors, social workers and salespersons are examples of such \emph{customer-facing} occupations. The third group of workers may need to be in physical proximity of one another even if they do not communicate, for example, to operate machinery or access key resources. Examples of such occupations requiring \emph{physical presence} are drivers and machine operators, especially in mining and water transport, where crammed working environments are common.

The spatial distribution of employment matters because face-to-face interactions are more frequent in dense cities \cite{Charlot2004-zr,Tian2019-wq}. So any social distancing intervention imposes disproportionately more limitation on urban sectors. We use our theory-motivated measures to estimate which sectors and which locations will be particularly hurt by social distancing.

\section*{A model of communication}
When workers communicate with others, they can divide labor more effectively. Production involves sequentially completing tasks indexed by $z\in[0,1]$. A single worker can do a range of tasks, but there is a benefit to specialization and division of labor \cite{Smith1778-qq,Becker1992-ac}. The labor cost of a worker completing $Z<1$ measure of tasks is $Z^{1+\gamma}/\gamma$, where $\gamma>0$ captures the benefits to the division of labor. As we show below, the higher the $\gamma$, the more specialized each worker will be in a narrower set of tasks. Without loss of generality, we normalize the wage rate of workers to one so that all costs are expressed relative to worker wages.

Once the range of tasks $Z$ is completed, the worker passes the unfinished product on to another worker. This has a cost of $\tau$, which can capture the cost of communicating and interacting across workers. The determinants of communication cost will be parametrized later. After all the tasks are completed, another step of communication with cost $\tau$ is needed to deliver the product to the customer. This cost leads to the Marshallian externality that firms want to be close to their customers and customers want to be close to their suppliers \cite{Marshall1920-ps,Krugman1991-gr}.

The firm will optimally decide how to share tasks between workers. The key trade-off is economizing on the cost of communication while exploiting the division of labor \cite{Becker1992-ac}. Let $n$ denote the number of workers involved in the production process. Because workers are symmetric, each works on $Z=1/n$ range of tasks before passing the work to the next worker. Production involves $n-1$ ``contacts'' (instances of communication) and there is an additional contact with the customer.

Fig \ref{fig1} illustrates the division of labor between workers. Horizontal movement represents production along a range of tasks ($Z=1/n$), vertical movement represents interaction ($\tau$). We note three potential interpretations of our model. First, when workers work in teams, they can efficiently divide labor among themselves (panel A). The benefit of a larger team is better specialization. Second, communication may involve the customer (panel B). The benefit of more frequent interaction with the customer is a product or service that is better suited to their needs. Third, workers may need access to a key physical resource, such as a machine, vehicle or an oil well (panel C). In this case, even if they do not communicate, they may be subject to social distancing measures. The key assumption behind all three interpretations is that frequent interaction increases productivity, whether happening between workers, between workers and customers, or between workers and machines.

\begin{figure}[!h]
\plos{\input{fig1a-input}\input{fig1b-input}\input{fig1c-input}}

\caption{{\bf Patterns of interaction in the workplace.}
Horizontal movement represents production, vertical movement represents interaction. (A) Each worker W works on a range $1/n$ of tasks, passing work $n-1$ times. (B) Worker W and customer C engage in frequent interactions. (C) Each worker W needs physical access to a key resource R.}
\label{fig1}
\end{figure}

The firm's cost minimization problem can then be written as a function of the number of contacts alone,
\begin{equation}\label{TC}
	c(\tau) = \min_n n\tau + \frac 1\gamma n^{-\gamma},
\end{equation}
where total communication costs are $n\tau$ and production costs are $n Z^{1+\gamma}/\gamma$ with $Z=1/n$.

Given the strict convexity of this cost function, and ignoring integer problems, the first-order condition is necessary and sufficient for the optimum,
\begin{equation}\label{nstar}
	n^*(\tau) = \tau^{-1/(1+\gamma)}.
\end{equation}
The number of worker contacts is decreasing in the cost of communication, expressed relative to worker wage. When the division of labor is important, $\gamma$ is high, and the number of contacts does not depend very strongly on communication costs.

The total cost of producing one good can be calculated by substituting in \eqref{nstar} into \eqref{TC},
\begin{equation}\label{cost}
	c(\tau) = \tau^{\chi}/\chi,
\end{equation}
where $\chi=\gamma/(1+\gamma)\in(0,1)$ measures the importance of division of labor. This unit cost function is the same as if workers and communication were substitutable in the production function in a Cobb-Douglas fashion. Indeed, $\chi$ captures the share of costs associated with communication and can be calibrated accordingly.

\subsection*{The cost of communication}
Businesses may differ in $\chi$, how important communication is in their production process. Another source of heterogeneity is the cost of communication between workers, which we specify further as follows.

When workers meet face to face, communication costs depend inversely on the population density in the neighborhood of the firm, $\tau=d^{-\varepsilon}$ with $\varepsilon>0$. This captures the Marshallian externality of knowledge spillovers \cite{Marshall1920-ps}, which happen more easily in densely populated areas \cite{Charlot2004-zr,Rossi-Hansberg2007-tm,Ioannides2008-bs,Tian2019-wq}. Contacts will be more frequent in dense areas,
\begin{equation}\label{communication}
	n^*(d) = d^{\varepsilon(1-\chi)}.
\end{equation}
The unit cost of production is
\begin{equation}\label{cost2}
c(d) = d^{-\varepsilon\chi}/\chi.
\end{equation}
Firms in dense areas face lower unit costs \cite{Ciccone1996-gu}, but this agglomeration benefit may be offset by higher wages and land rents in places with high population density \cite{Eberts1982-zf,Madden1985-pq,Combes2019-ud}. In spatial equilibrium (not modeled here), firms with high communication needs will choose to locate in high-density areas \cite{Tian2019-wq}.

\subsection*{Social distancing measures}
We study the effect of a social distancing intervention that puts an upper limit $N$ on the number of face-to-face contacts. Firms can mitigate the disruption from this measure by moving communication online, but this is more costly per contact than face-to-face communication.

The optimal number of contacts without social distancing is given by Eq \eqref{communication}. Firms with $n^*>N$ are limited by social distancing. Without moving communication online, their unit cost will increase to $c' = N d^{-\varepsilon} + N^{-\gamma}/\gamma$, which is greater than the optimal cost,
\begin{equation}\label{socdist}
\frac{c'(d)}{c(d)} 
	= \chi \frac{N}{n^*(d)} + (1-\chi) \left(\frac{N}{n^*(d)}\right)^{-\gamma}>1.
\end{equation}
The first term of the weighted average is less than one, representing a reduction in communication costs once the number of contacts is limited. The second term is greater than one due to the fact that every worker has to complete a wider range of tasks than before, and they lose the benefit of specialization. Because $n^*$ is the cost-minimizing communication choice of the firm, the second term dominates, and production costs increase with social distancing.

If the firm chooses to use telecommunication, the cost per contact will be $T>d^{\varepsilon}$ (otherwise the firm would have used telecommunication before). The proportional increase in production costs in this case is given by
\begin{equation}\label{telco}
\frac{c''(d)}{c(d)} 
	= T^\chi d^{\varepsilon \chi}
	>1.
\end{equation}
In both cases, the cost increase is highest for communication-intensive firms (large $\gamma$ and $\chi$) and those operating in a high-density area (high $d$ and hence high $n^*$).

Fig \ref{fig2} displays the ratio of production costs under social distancing to the optimal production costs as a function of density. Firms in low-density areas are unaffected by social distancing since they do not have many contacts anyway. Those in intermediate-density areas would suffer less of a cost increase by switching to telecommunication. Firms in the highest-density areas will stick to face-to-face communication, which is still the more efficient form of communication despite restrictions. However, they will suffer the greatest cost increase.

\begin{figure}[!h]
\plos{\centering\input{fig2-input}}

\caption{{\bf Both social distancing and telecommunication hurt firms in dense areas more.}
See Eq \eqref{socdist} and Eq \eqref{telco} for the relative production costs under the two interventions.}
\label{fig2}
\end{figure}

\section*{Data and methodology}
To estimate the potential disruptions from social distancing, we need a measure of the importance of worker interaction (corresponding to $\chi$ in the model) and its cost (captured by population density $d$).

Let $\xi_o$ denote an indicator equal to one if occupation $o$ is interaction-intensive and zero otherwise. For industry $i$, $\chi_i = \sum_o s_{io}\xi_o$ measures the fraction of workers in affected occupations, with $s_{io}$ denoting the employment share of occupation $o$ in industry $i$.

We use the Occupational Information Network (O*NET) \cite{National_Center_for_ONET_Development2020-wj} to measure the characteristics of a given occupation, similarly to previous studies \cite{Firpo2011-hp,Autor2013-sh,Jin2020-tq,Dingel2020-lh,Leibovici2020-qr,Mongey2020-qc}. The O*NET dataset contains detailed standardized descriptions on almost 1,000 occupations along eight dimensions. We focus on job characteristics that are related to recent social distancing measures, while prior work focused mainly on measuring offshorability of the given tasks \cite{Firpo2011-hp,Autor2013-sh}.

Social distancing interventions limit the interaction between people and regulate physical proximity between individuals. We thus focus on three related job characteristics based on work context and work activity described in O*NET. The first two indicators capture how communication-intensive the job is. Communication can be of two types: internal communication with co-workers (\emph{teamwork}) or external communication directly with customers (\emph{customer-facing}). The third indicator takes into consideration the possibility that workers may need to be in physical proximity of one another even if they do not communicate. We create an index that shows how important \emph{physical presence} is to perform a given job. Table \ref{table1} details the specific O*NET indexes that contribute to each of our three measures.
As social distancing measures only limit personal communication, for communication indexes, we require that the necessary face-to-face communication happens at least several times a week. 
In teamwork, face-to-face meetings can often be substituted by more structured communication, for which working from home is not as disruptive. To allow for this possibility, we only classify occupations as teamwork-intensive where both emails and letters and memos are less frequent forms of communication than face-to-face meetings. This excludes most managers and certain business services. Similarly, for physical presence, we require at least a certain degree of proximity to other workers which corresponds to working in a shared office.

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Definition of social distancing indexes.}}
\begin{tabular}{|l|l|l|}
\hline
{\bf Index} & {\bf Tasks} & {\bf Context} 
\\ \thickhline
\hline
Teamwork & Work With Work Group or Team & Face-to-face  \\
& Provide Consultation and Advice to Others & discussions  \\
& Coordinating the Work and Activities of Others & several times a week \\
& Guiding Directing and Motivating Subordinates & \& more often than \\
& Developing and Building Teams & emails, letters, memos\\
\hline
Customer & Deal With External Customers & Face-to-face\\
&  Performing for or Working Directly with the Public & discussions \\
& Assisting and Caring for Others & several \\
& Provide Consultation and Advice to Others & times a week\\
& Establishing and Maintaining Interpersonal Relationships &\\
\hline
Presence & Handling and Moving Objects & Density of \\
& Operating Vehicles, Mechanized Devices or Equipment & co-workers \\
& Repairing and Maintaining Electronic Equipment &  like shared\\
& Repairing and Maintaining Mechanical Equipment & office or more\\
& Inspecting Equipment, Structures, or Material &\\
\hline
\hline
\end{tabular}
\begin{flushleft} Each social distancing index (column 1) is created as an arithmetic average of the component indexes (column 2). To be classified an affected occupation, the average has to exceed 62.5 and the work context index has to exceed the threshold in column 3.
\end{flushleft}
\label{table1}
%\end{adjustwidth}
\end{table}

We aggregate the measures to 6-digit occupation codes (Standard Occupational Classification; 2010-SOC). We have information on the relevance of teamwork, customer contact and physical presence  for 809 occupations in SOC 2010 codes.

Teamwork and customer contacts are highly correlated (Fig \ref{fig3}), but they are conceptually different. While all medical occupations require teamwork and customer contact, supervisors in general are working in teams but do not often communicate directly with customers. Machine operators and production workers in general are at the bottom of both of the distributions. As managers can substitute personal communication with emails, they are not considered in general as teamwork-intensive occupations according to our definition. Given the high correlation between the two types of communication, we often refer to \emph{communication-intensive} occupations that are either teamwork-intensive or customer-facing.

\begin{figure}[!h]
\plos{\includegraphics[width=0.7\linewidth]{fig3.pdf}}

\caption{{\bf Teamwork and customer contact are highly correlated.}
Each circle represents an occupation. Teamwork and customer contact indexes are constructed as explained in main text.}
\label{fig3}
\end{figure}

As a next step, we calculate for each sector the share of workers whose job requires a high level of teamwork, customer contact and physical presence. 
We use the same sectoral breakdown as the Current Employment Statistics (CES) \cite{CES}. As all the indexes are an absolute value running from 0 to 100, we use 62.5 as a cutoff to define a job to be teamwork-intensive, customers contact-intensive or job that require physical presence from the worker.  The occupation structure of the industries are retrieved from the official industry-occupation matrix \cite{employment-matrix}, we use the employment statistics by occupation-industry for February 2020.

Based on the share of relevant occupations in industry employment, the most teamwork-intensive sectors are, for example ``Hospitals,'' ``Accommodation'' and  ``Motion picture and sound recording industries.'' In contrast, teamwork is not important in sectors like ``Forestry and logging'' and ``Fishing, hunting and trapping.''  Customer contact is relevant in sectors like ``Hospitals''  and ``Retail'', while it is not relevant is sectors line ``Truck transportation,'' and ``Forestry and logging.'' Physical presence is relevant in sectors like  ``Truck transportation,'' ``Repair and maintenance,'' mining in general, while it is not relevant in finance and information technology sectors.

``Hospitals'' score high on all three measures because communication in health care teams and with patients is important, and doctors and nurses work in close physical proximity to others. We nonetheless remove this sector from the analysis because of its inevitable direct role in combating the epidemic which is not captured well in a simple model of communication.

To measure the heterogeneity in the cost of communication, we measure population density in the neighborhood of businesses. The assumption in the model is that communication costs are lower in dense areas. This is consistent with the fact that communication-intensive sectors such as business services and advertising, together with central administrative offices of production firms tend to be concentrated in high-density areas \cite{Aarland2007-dh}.

The location of sectors comes from the County Business Patterns (CBP) data for 2017 \cite{CBP}. For a finer spatial resolution, we use the data tabulated by ZIP-Code Tabulation Areas. The CBP lists the number of establishments of a certain size for each ZIP-code and NAICS industry code. Because establishment sizes are given in bins (e.g., 1--4 employees), we take the midpoint of each bin as our estimated employment (e.g., 2.5 employees). In small industries and ZIP codes, the Census omits some size categories to protect the confidentiality of businesses. We impute employment in these plants from the national size distribution of plants in the same NAICS industry. Our estimated industry-level employment is a very good approximation to official employment statistics \cite{CES}. The correlation between our estimates based on CBP and the employment reported in CES is 0.98.

To understand the heterogeneity across regions, we average the share of workers in teamwork-intensive, customer-facing and physical presence occupations across industries active in each ZIP code. For each of the three occupation groups, let $\xi_{og}$ denote the indicator whether occupation $o$ belongs to group $g$. The industry share of workers in the occupation group is given by $\sum_o s_{io}\xi_{og}$. We compute the regional share of the occupation group as an employment-weighted average across industries, $\sum_i l_{ir}\sum_o s_{io}\xi_{og}/\sum_i l_{ir}$, where $l_{ir}$ is the estimated employment of industry $i$ in region (ZIP code) $r$. Because we only have industry but not occupation data by location, we have assumed that the occupation distribution within the sector, $s_{io}$, does not vary across locations. The fact that the CBP tabulates employment by establishments rather than firms makes this a good approximation. For example, a sporting good producer may also have an administrative office and a retail store in different locations, but these will be classified in their respective NAICS sectors rather than in sporting good manufacturing.

We use population density to measure how locations differ in the costs of communication. We also experimented with using employment densities instead of population densities. Results were very similar, as the two measures are highly correlated with the exception of very high employment-density urban centers where population is more sparse \cite{Heblich2017-lb}.

\subsection*{Counterfactual calculations}
To gauge the magnitude of the effect of social distancing, we calibrate the parameters of the model and compute the effect of a policy that limits the number of worker contacts. At the same time, we let the government introduce a proportional wage subsidy $\lambda$ to help offset the costs from lower interaction. With this subsidy, the cost of labor will be $(1-\lambda)$. We ask what level of $\lambda$ would compensate businesses for the communication disruption caused by social distancing. Using the cost change in Eq \ref{socdist}, we can express
\begin{equation}\label{subsidy}
    \lambda_{ir} = 1 -
        \frac{1-\chi_i}{1-\chi_i N/n_{ir}^*}
        \left(
        \frac{N}{n_{ir}^*}
        \right)^{\gamma_i}>0.
\end{equation}
The compensating wage subsidy increases in the importance of communication $\chi_i$ and the optimal number of contacts $n^*_{ir}$, and decreases in the number of allowed contacts $N$. The subscripts note that communication share is industry specific and the optimal number of contacts is both industry and region specific.

We calibrate the upper limit on personal contacts $N$ such that the overall number of contacts in the economy, when averaged across ZIP codes and industries, is reduced by half, $\sum_{i,r}l_{ir}\min\{N,n_{ir}^*\} = 0.5\sum_{i,r}l_{ir}n_{ir}^*$. Due to the inherent nonlinearity of the model, other interventions will have different effects.

To calibrate the importance of communication $\chi_i$, note that it is the cost share of communication, and can be correspondingly calibrated to the employment share of communication-intensive occupations in industry $i$. Here we take all occupations that are either teamwork intensive or customer facing.

Population density in region $r$ can be measured directly in the data, as explained above.
The only remaining parameter to calibrate is the elasticity of the communication externality $\varepsilon$. We rely on previous estimates of agglomeration effects that capture the elasticity of total factor productivity with respect to population density \cite{Ciccone1996-gu}. In our model, the elasticity of unit costs (which can be construed as the inverse of productivity) with respect to density is $-\varepsilon\chi$ (Eq \eqref{cost2}). We calibrate $\varepsilon=0.02$ so that, across all ZIP codes and industries, a regression of log model-implied productivity ($\varepsilon\chi_i\ln d_r$) on log population density $\ln d_r$ yields an elasticity of 0.04 \cite[page 60]{Ciccone1996-gu}.

Given these parameter values, we compute the compensating wage subsidy for each industry in each ZIP code using Eq \ref{subsidy}. We report employment-weighted averages of this across sectors and across locations.

\section*{Results}
Table \ref{table2} displays the top five and the bottom five industries by 2-digit NAICS industries as sorted by the percentage of workers in communication-intensive occupations, excluding hospitals and clinics. Across industries, retail trade, accommodation and food services, arts, entertainment, and recreation, other services and educational services have the highest share of communication-intensive workers, exceeding 35 percent. Transportation, production, construction and agricultural industries are less reliant on face-to-face communication. This heterogeneity across industries is important to understand the effect of social distancing measures.

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Retail, professional services, finance and restaurants are the most communication intensive.}}
\begin{tabular}{|l|c|c|c|c|}
\hline
 & \multicolumn{3}{c}{\bf Communication} &  
\\ 
{\bf Industry} & {\bf Teamw.} & {\bf Custom.} & {\bf Overall} & {\bf Presence} 
\\ \thickhline
Retail trade &13&67&68&5\\
Accommodation \& food services &8&50&51&1\\
Arts, Entertainment, and Recreation &12&40&42&2\\
Other Services (except Public Admin.) &12&38&41&12\\
Educational Services &15&35&37&1\\
...&&&&\\
Wholesale Trade &8&16&20&12\\
Transportation and Warehousing  &8&10&16&32\\
Manufacturing &7&6&11&10\\
Construction &15&5&18&28\\
Agri., forestry, fishing \& hunting &4&4&7&23\\
 \thickhline

\hline
\end{tabular}
\begin{flushleft} ``Teamw.'' and ``Custom.'' show the percentage of workers in teamwork-intensive and customer-facing occupations, respectively. ``Overall'' shows the percentage of workers in communication-intensive occupations that are either teamwork-intensive or customer-facing. It is less than the sum of the two indexes because some occupations rely on both types of communication. ``Presence'' shows the percentage of workers whose jobs require physical presence in close proximity to others.
\end{flushleft}
\label{table2}
%\end{adjustwidth}
\end{table}

Fig \ref{fig4} plots the share of workers in the three affected occupation groups across ZIP codes by population density. Customer-facing occupations are overrepresented in dense areas. In the highest population density ZIP codes, 43 percent of workers are employed in customer-facing occupations. Teamwork-intensive occupations are broadly distributed in space.

\begin{figure}[!h]
\plos{\includegraphics[width=0.7\linewidth]{fig4.pdf}}

\caption{{\bf Urban areas employ more workers in customer-facing occupations, less in occupations requiring physical presence.}
Locally weighted polynomial regression of average share of teamwork-intensive occupations, customer-facing occupations and occupations requiring physical presence across sectors within the ZIP code (bandwidth $=0.5$).}
\label{fig4}
\end{figure}

In the calibrated model, a social distancing policy that puts a cap on interactions per worker such that the total number of interactions drops by half nationwide is compensated a 12.2 percent wage subsidy. The distribution of the compensating wage subsidy is, however, unequal over space and across industries. 
New York City, with a population density about 20 times the average U.S. city, would require a 13.3 percent wage subsidy. 
By contrast, the compensating wage subsidy in agriculture, transportation and manufacturing would be less than 6 percent (Table \ref{table3}).

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf The five most affected sectors require more than 20 percent wage subsidy.}}
\begin{tabular}{|l|c|c|}
\hline
{\bf Industry} & {\bf Wage subsidy} & {\bf Employment} 
\\ \thickhline
Retail Trade	&22.1	&15,659\\
Accommodation and Food Services	&17.7	&14,379\\
Arts, Entertainment, and Recreation	&15.1	&2,494\\
Other Services (except Public Admin.)	&14.5	&5,939\\
Educational Services	&13.8	&3,838\\
...&&\\
Wholesale Trade	&7.7	&5,936\\
Construction	&6.8	&7,646\\
Transportation and Warehousing	&5.9	&5,523\\
Manufacturing	&4.5	&12,861\\
Agriculture, Forestry, Fishing and Hunting	&2.6	&55\\
\hline
{\bf Average} & {\bf 12.2} & {\bf 116,496}\\
 \thickhline

\hline
\end{tabular}
\begin{flushleft} ``Wage subsidy'' displays the percentage decrease in labor costs necessary to compensate businesses when worker contacts are reduced by half. ``Employment'' is the February 2020 employment of the sector in thousands \cite{CES}. The last row shows the employment-weighted average wage subsidy. Table excludes hospitals, clinics, and government establishments which are not present in CBP.
\end{flushleft}
\label{table3}
%\end{adjustwidth}
\end{table}

\section*{Discussion and conclusions}
The main cost of social distancing in our model is insufficient division of labor. This mechanism is motivated by \cite{Smith1778-qq} and captures the same trade-off as \cite{Becker1992-ac}. Our contribution is specifying the cost function in such a way that can be easily mapped to the data.

More broadly, our argument is that frequent interaction increases productivity irrespective whether it is happening between workers, between workers and customers, or between workers and machines. In the main part of the empirical analysis, we focused only on the first two types of interactions, while we were silent about the third. But social distancing measures also affect sectors where workers need to be in physical proximity of one another even if they do not communicate, for example, to operate machinery or access key resources. This is relevant in sectors like ``Mining, Quarrying, and Oil and Gas Extraction'' and ``Transportation'' while it is not relevant in sectors like ``Finance and Insurance'' and ``Professional, Scientific, and Technical Services.'' As can be seen from Fig \ref{fig4}, occupations requiring physical presence have the highest share in less dense areas where production and mining plants are located. (Farms are not included in the CBP.) The share of these occupations in the most dense areas is only 3 percent.

To a greater or lesser extent, all sectors will be affected by social distancing. Some sectors are hit by the intervention due to restricted face-to-face communication, others are hit due to restricting physical proximity of people. Some sectors are less affected across all dimensions. Examples include ``Fishing, hunting and trapping,'' ``Printing and related support activities,'' and manufacturing in general.

Our results are consistent with parallel research on the overall economic effects of the coronavirus pandemic using O*NET data. Recent research found that about 34 percent of U.S. jobs can be performed from home \cite{Dingel2020-lh}. However, as our analysis points out, even among jobs that do not fall into this category, some are more at risk from social distancing than others. The share of workers working in close physical proximity to other people is similar to other recent estimates \cite{Leibovici2020-qr}. Workers in this group are found to be the most vulnerable across a wide range of socio-economic measures \cite{Jin2020-tq,Mongey2020-qc}. We contribute to this work by (i) building a model to understand how social distancing measures affect the production, (ii) identifying three groups of occupations affected by social distancing and (iii) taking into account the disproportionate costs borne by urban sectors.

We see four avenues for further research. The first concerns the demand side of the economy, which we have mostly neglected by focusing on the production function. The employment response to a production disruption greatly depends on the elasticity of demand. We hypothesize that sectors like schooling and health care have inelastic demand and will continue to employ many workers despite significant disruptions. However, personal services, small grocery stores and restaurants may face more elastic demand and respond to large production cost increases by laying off a significant fraction of their work force.

The second direction concerns the interaction between sectors and regions. Whenever productivity in any business drops, this shock can propagate to its buyers and suppliers. The aggregate consequences of the epidemic will hence be modulated by input-output linkages between sectors, regions and countries \cite{Caliendo2014-mr,Caselli2020-nf,Baldwin2020-wb}.

The third and forth directions concern the long-run response of businesses as they try to become more resilient to such shocks in the future. Whether the share of telecommunication remains large in the long run depends crucially on how easily it substitutes for face-to-face interaction. In our model, the two are perfect substitutes with the only distinction that the efficiency of face-to-face meetings improves with population density, whereas telecommunication does not depend on agglomeration \cite{Rossi-Hansberg2007-tm,Ioannides2008-bs,Tian2019-wq}. Previous work has found face-to-face communication to be more effective in high-intensity communication which is particularly helpful to overcome incentive problems in joint production \cite{Gaspar1998-gy,Storper2004-mg}. Data on internet flows suggests that telecommunication is not a good substitute for face-to-face meetings \cite{Cuberes2013-js}. None of these papers discuss disruptions from social distancing measures. Further study of the modes of communication in the O*NET occupation survey can shed light on whether telecommunication can act as a low-cost substitute for face-to-face meetings.

Fourth, businesses may change their location in response to perceived threats and disruptions. As we discussed, epidemics have a disproportionate effect on cities. So it is conceivable that in a post-pandemic spatial equilibrium (not modeled here, but see \cite{Tian2019-wq}), the agglomeration premium falls and firms find it less attractive to locate in cities. A poignant point of comparison is the increased threat of terrorism in major cities following devastating attacks on New York, Washington, London, Paris, Madrid, Moscow and Mumbai. The general conclusion about terror threat is that cities have remained resilient and a robust attractor of businesses \cite{Glaeser2002-mw,Harrigan2002-ik}. We speculate that epidemics and social distancing can be more detrimental to cities than terror threats, because they tear apart the very fabric of urban life. However, we have limited data to make further predictions.

\section*{Supporting information}

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Full table of sectors.}
\label{S1_File}
{\bf Social distancing exposure by sector.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the industry. ``Communucation share'' refers to the share of workers who are either teamwork-intensive or customer-facing. ``Affected share'' refers to the share of workers in any of the three occupation groups. Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v1.3/data/derived/industry-index.csv}.

\paragraph*{S2 Full table of ZIP-codes.}
\label{S2_File}
{\bf Social distancing exposure by location.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the ZIP code. ``Communucation share'' refers to the share of workers who are either teamwork-intensive or customer-facing. ``Affected share'' refers to the share of workers in any of the three occupation groups. Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v1.3/data/derived/location-index.csv}.

\paragraph*{S3 Data repository.}
\label{S3_URL}
{\bf Replication code and data.} Replication code and data are available at \url{https://github.com/ceumicrodata/social-distancing/tree/v1.3}.

\section*{Acknowledgments}
We thank Gábor Békés, Péter Harasztosi, Péter Karádi, Balázs Lengyel, Dávid Krisztián Nagy, Andrea Weber, Charles Wyplosz, and an anonymous referee for comments.

\nolinenumbers

%\begin{thebibliography}{10}

%\end{thebibliography}

### 2020-06-29 text/regression.tex
Add regression tables with 4 columns
References #9

{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabular}{l*{4}{D{.}{.}{-1}}}
\hline\hline
                    &\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
                    &\multicolumn{1}{c}{Employment change (log)}&\multicolumn{1}{c}{Employment change (log)}&\multicolumn{1}{c}{Employment change (log)}&\multicolumn{1}{c}{Employment change (log)}\\
\hline
Customer-facing workers (share, [0,1])&      -0.286\sym{**} &                     &                     &                     \\
                    &     (0.138)         &                     &                     &                     \\
[1em]
   of which face-to-face intensive&                     &      -0.409\sym{**} &      -0.453\sym{***}&      -0.240\sym{**} \\
                    &                     &     (0.158)         &     (0.142)         &     (0.110)         \\
[1em]
Teamwork-intensive workers (share, [0,1])&       0.690\sym{***}&                     &                     &                     \\
                    &     (0.158)         &                     &                     &                     \\
[1em]
   of which face-to-face intensive&                     &       0.107         &       0.343         &       1.204\sym{**} \\
                    &                     &     (0.531)         &     (0.486)         &     (0.487)         \\
[1em]
Presence-intensive workers (share, [0,1])&       0.227\sym{**} &                     &                     &                     \\
                    &     (0.103)         &                     &                     &                     \\
[1em]
   of which in close proximity to others&                     &       0.079         &      -0.053         &       0.083         \\
                    &                     &     (0.120)         &     (0.128)         &     (0.091)         \\
[1em]
Change in number of monthly visits (log)&                     &                     &       0.188\sym{***}&       0.644\sym{***}\\
                    &                     &                     &     (0.059)         &     (0.129)         \\
[1em]
   X share can work from home (customer)&                     &                     &                     &       0.001         \\
                    &                     &                     &                     &     (0.164)         \\
[1em]
   X share can work from home (teamwork)&                     &                     &                     &      -0.881\sym{***}\\
                    &                     &                     &                     &     (0.217)         \\
\hline
Observations        &          79         &          79         &          78         &          78         \\
\(R^{2}\)           &       0.248         &       0.183         &       0.307         &       0.593         \\
\hline\hline
\end{tabular}
}

### 2020-06-29 text/regression.tex
Keep only presence_interact_share, as for physical workers, working from home does not make sense
Re #9

@@
 \hline
-Customer-facing workers (share, [0,1])&      -0.286\sym{**} &                     &                     &                     \\
+Customer-facing workers (share, [0,1])&      -0.293\sym{**} &                     &                     &                     \\
                     &     (0.138)         &                     &                     &                     \\
@@
 [1em]
-Teamwork-intensive workers (share, [0,1])&       0.690\sym{***}&                     &                     &                     \\
-                    &     (0.158)         &                     &                     &                     \\
+Teamwork-intensive workers (share, [0,1])&       0.677\sym{***}&                     &                     &                     \\
+                    &     (0.156)         &                     &                     &                     \\
 [1em]
@@
 [1em]
-Presence-intensive workers (share, [0,1])&       0.227\sym{**} &                     &                     &                     \\
-                    &     (0.103)         &                     &                     &                     \\
-[1em]
-   of which in close proximity to others&                     &       0.079         &      -0.053         &       0.083         \\
-                    &                     &     (0.120)         &     (0.128)         &     (0.091)         \\
+Presence-intensive workers (share, [0,1])&       0.224\sym{**} &       0.079         &      -0.053         &       0.083         \\
+                    &     (0.111)         &     (0.120)         &     (0.128)         &     (0.091)         \\
 [1em]
@@
 Observations        &          79         &          79         &          78         &          78         \\
-\(R^{2}\)           &       0.248         &       0.183         &       0.307         &       0.593         \\
+\(R^{2}\)           &       0.245         &       0.183         &       0.307         &       0.593         \\
 \hline\hline

### 2020-06-30 text/regression.tex
Update regression table with new interaction terms
Also remove column titles. Re #9

@@
                     &\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
-                    &\multicolumn{1}{c}{Employment change (log)}&\multicolumn{1}{c}{Employment change (log)}&\multicolumn{1}{c}{Employment change (log)}&\multicolumn{1}{c}{Employment change (log)}\\
+                    &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} \\
 \hline
@@
 [1em]
-   of which face-to-face intensive&                     &      -0.409\sym{**} &      -0.453\sym{***}&      -0.240\sym{**} \\
-                    &                     &     (0.158)         &     (0.142)         &     (0.110)         \\
+--of which face-to-face intensive&                     &      -0.409\sym{**} &      -0.453\sym{***}&       0.066         \\
+                    &                     &     (0.158)         &     (0.142)         &     (0.155)         \\
 [1em]
@@
 [1em]
-   of which face-to-face intensive&                     &       0.107         &       0.343         &       1.204\sym{**} \\
-                    &                     &     (0.531)         &     (0.486)         &     (0.487)         \\
+--of which face-to-face intensive&                     &       0.107         &       0.343         &       0.400         \\
+                    &                     &     (0.531)         &     (0.486)         &     (0.760)         \\
 [1em]
-Presence-intensive workers (share, [0,1])&       0.224\sym{**} &       0.079         &      -0.053         &       0.083         \\
-                    &     (0.111)         &     (0.120)         &     (0.128)         &     (0.091)         \\
+Presence-intensive workers (share, [0,1])&       0.224\sym{**} &       0.079         &      -0.053         &       0.005         \\
+                    &     (0.111)         &     (0.120)         &     (0.128)         &     (0.107)         \\
 [1em]
-Change in number of monthly visits (log)&                     &                     &       0.188\sym{***}&       0.644\sym{***}\\
-                    &                     &                     &     (0.059)         &     (0.129)         \\
+Change in number of monthly visits (log)&                     &                     &       0.188\sym{***}&      -0.084         \\
+                    &                     &                     &     (0.059)         &     (0.122)         \\
 [1em]
-   X share can work from home (customer)&                     &                     &                     &       0.001         \\
-                    &                     &                     &                     &     (0.164)         \\
+--times customer-facing share&                     &                     &                     &       1.105\sym{***}\\
+                    &                     &                     &                     &     (0.379)         \\
 [1em]
-   X share can work from home (teamwork)&                     &                     &                     &      -0.881\sym{***}\\
-                    &                     &                     &                     &     (0.217)         \\
+--times teamwork-intensive share&                     &                     &                     &      -0.118         \\
+                    &                     &                     &                     &     (1.270)         \\
 \hline
 Observations        &          79         &          79         &          78         &          78         \\
-\(R^{2}\)           &       0.245         &       0.183         &       0.307         &       0.593         \\
+\(R^{2}\)           &       0.245         &       0.183         &       0.307         &       0.452         \\
 \hline\hline

### 2020-06-30 text/regression.tex
Wrap variable names in regression Table
Re #9

@@
 \hline
-Customer-facing workers (share, [0,1])&      -0.293\sym{**} &                     &                     &                     \\
-                    &     (0.138)         &                     &                     &                     \\
+Customer-facing     &      -0.293\sym{**} &                     &                     &                     \\
+workers (share, [0,1])&     (0.138)         &                     &                     &                     \\
 [1em]
---of which face-to-face intensive&                     &      -0.409\sym{**} &      -0.453\sym{***}&       0.066         \\
-                    &                     &     (0.158)         &     (0.142)         &     (0.155)         \\
+--of which          &                     &      -0.409\sym{**} &      -0.453\sym{***}&       0.066         \\
+face-to-face intensive&                     &     (0.158)         &     (0.142)         &     (0.155)         \\
 [1em]
-Teamwork-intensive workers (share, [0,1])&       0.677\sym{***}&                     &                     &                     \\
-                    &     (0.156)         &                     &                     &                     \\
+Teamwork-intensive  &       0.677\sym{***}&                     &                     &                     \\
+workers (share, [0,1])&     (0.156)         &                     &                     &                     \\
 [1em]
---of which face-to-face intensive&                     &       0.107         &       0.343         &       0.400         \\
-                    &                     &     (0.531)         &     (0.486)         &     (0.760)         \\
+--of which          &                     &       0.107         &       0.343         &       0.400         \\
+face-to-face intensive&                     &     (0.531)         &     (0.486)         &     (0.760)         \\
 [1em]
-Presence-intensive workers (share, [0,1])&       0.224\sym{**} &       0.079         &      -0.053         &       0.005         \\
-                    &     (0.111)         &     (0.120)         &     (0.128)         &     (0.107)         \\
+Presence-intensive  &       0.224\sym{**} &       0.079         &      -0.053         &       0.005         \\
+workers (share, [0,1])&     (0.111)         &     (0.120)         &     (0.128)         &     (0.107)         \\
 [1em]
-Change in number of monthly visits (log)&                     &                     &       0.188\sym{***}&      -0.084         \\
-                    &                     &                     &     (0.059)         &     (0.122)         \\
+Change in number of &                     &                     &       0.188\sym{***}&      -0.084         \\
+monthly visits (log)&                     &                     &     (0.059)         &     (0.122)         \\
 [1em]
---times customer-facing share&                     &                     &                     &       1.105\sym{***}\\
-                    &                     &                     &                     &     (0.379)         \\
+--times             &                     &                     &                     &       1.105\sym{***}\\
+customer-facing share&                     &                     &                     &     (0.379)         \\
 [1em]
---times teamwork-intensive share&                     &                     &                     &      -0.118         \\
-                    &                     &                     &                     &     (1.270)         \\
+--times             &                     &                     &                     &      -0.118         \\
+teamwork-intensive share&                     &                     &                     &     (1.270)         \\
 \hline

### 2020-06-30 text/regression.tex
Reformat regression table to fit in PLOS column width
Resolves #9

@@
-{
-\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-\begin{tabular}{l*{4}{D{.}{.}{-1}}}
-\hline\hline
+{\setlength{\tabcolsep}{0pt}
+{\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}\begin{tabular}{l*{4}{D{.}{.}{-1}}}\hline\hline
                     &\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
@@
 \hline
-Customer-facing     &      -0.293\sym{**} &                     &                     &                     \\
-workers (share, [0,1])&     (0.138)         &                     &                     &                     \\
+Customer-facing~workers&      -0.293\sym{**} &                     &                     &                     \\
+(share, [0,1])      &     (0.138)         &                     &                     &                     \\
 [1em]
---of which          &                     &      -0.409\sym{**} &      -0.453\sym{***}&       0.066         \\
-face-to-face intensive&                     &     (0.158)         &     (0.142)         &     (0.155)         \\
+--of~which~face-to-face&                     &      -0.409\sym{**} &      -0.453\sym{***}&       0.066         \\
+intensive           &                     &     (0.158)         &     (0.142)         &     (0.155)         \\
 [1em]
-Teamwork-intensive  &       0.677\sym{***}&                     &                     &                     \\
-workers (share, [0,1])&     (0.156)         &                     &                     &                     \\
+Teamwork-intensive~workers&       0.677\sym{***}&                     &                     &                     \\
+(share, [0,1])      &     (0.156)         &                     &                     &                     \\
 [1em]
---of which          &                     &       0.107         &       0.343         &       0.400         \\
-face-to-face intensive&                     &     (0.531)         &     (0.486)         &     (0.760)         \\
+--of~which~face-to-face&                     &       0.107         &       0.343         &       0.400         \\
+intensive           &                     &     (0.531)         &     (0.486)         &     (0.760)         \\
 [1em]
-Presence-intensive  &       0.224\sym{**} &       0.079         &      -0.053         &       0.005         \\
-workers (share, [0,1])&     (0.111)         &     (0.120)         &     (0.128)         &     (0.107)         \\
+Presence-intensive~workers&       0.224\sym{**} &       0.079         &      -0.053         &       0.005         \\
+(share, [0,1])      &     (0.111)         &     (0.120)         &     (0.128)         &     (0.107)         \\
 [1em]
-Change in number of &                     &                     &       0.188\sym{***}&      -0.084         \\
+Change~in~number~of &                     &                     &       0.188\sym{***}&      -0.084         \\
 monthly visits (log)&                     &                     &     (0.059)         &     (0.122)         \\
 [1em]
---times             &                     &                     &                     &       1.105\sym{***}\\
-customer-facing share&                     &                     &                     &     (0.379)         \\
+--times~customer-facing~share&                     &                     &                     &       1.105\sym{***}\\
+                    &                     &                     &                     &     (0.379)         \\
 [1em]
---times             &                     &                     &                     &      -0.118         \\
-teamwork-intensive share&                     &                     &                     &     (1.270)         \\
+--times~teamwork-intensive~share&                     &                     &                     &      -0.118         \\
+                    &                     &                     &                     &     (1.270)         \\
 \hline

### 2020-06-30 text/regression.tex
Change typesetting of regression table

--- 2020-06-30 text/regression.tex
@@
-{
-\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-\begin{tabular}{l*{4}{D{.}{.}{-1}}}
-\hline\hline
+{\setlength{\tabcolsep}{-2pt}
+{\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}\begin{tabular}{l*{4}{D{.}{.}{-1}}}\hline\hline
                     &\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
@@
 \hline
-Customer-facing     &      -0.293\sym{**} &                     &                     &                     \\
-workers (share, [0,1])&     (0.138)         &                     &                     &                     \\
+Customer-facing~workers&      -0.293\sym{**} &                     &                     &                     \\
+\hspace*{1em}(share, [0,1])&     (0.138)         &                     &                     &                     \\
 [1em]
---of which          &                     &      -0.409\sym{**} &      -0.453\sym{***}&       0.066         \\
-face-to-face intensive&                     &     (0.158)         &     (0.142)         &     (0.155)         \\
+\hspace*{1em}of~which~face-to-face&                     &      -0.409\sym{**} &      -0.453\sym{***}&       0.066         \\
+\hspace*{1em}intensive (share, [0,1])&                     &     (0.158)         &     (0.142)         &     (0.155)         \\
 [1em]
-Teamwork-intensive  &       0.677\sym{***}&                     &                     &                     \\
-workers (share, [0,1])&     (0.156)         &                     &                     &                     \\
+Teamwork-intensive~workers&       0.677\sym{***}&                     &                     &                     \\
+\hspace*{1em}(share, [0,1])&     (0.156)         &                     &                     &                     \\
 [1em]
---of which          &                     &       0.107         &       0.343         &       0.400         \\
-face-to-face intensive&                     &     (0.531)         &     (0.486)         &     (0.760)         \\
+\hspace*{1em}of~which~face-to-face&                     &       0.107         &       0.343         &       0.400         \\
+\hspace*{1em}intensive (share, [0,1])&                     &     (0.531)         &     (0.486)         &     (0.760)         \\
 [1em]
-Presence-intensive  &       0.224\sym{**} &       0.079         &      -0.053         &       0.005         \\
-workers (share, [0,1])&     (0.111)         &     (0.120)         &     (0.128)         &     (0.107)         \\
+Presence-intensive~workers&       0.224\sym{**} &       0.079         &      -0.053         &       0.005         \\
+\hspace*{1em}(share, [0,1])&     (0.111)         &     (0.120)         &     (0.128)         &     (0.107)         \\
 [1em]
-Change in number of &                     &                     &       0.188\sym{***}&      -0.084         \\
-monthly visits (log)&                     &                     &     (0.059)         &     (0.122)         \\
+Change~in~number~of &                     &                     &       0.188\sym{***}&      -0.084         \\
+\hspace*{1em}monthly visits (log)&                     &                     &     (0.059)         &     (0.122)         \\
 [1em]
---times             &                     &                     &                     &       1.105\sym{***}\\
-customer-facing share&                     &                     &                     &     (0.379)         \\
+\hspace*{1em}$\times$~customer-facing~share&                     &                     &                     &       1.105\sym{***}\\
+\hspace*{1em}([0,1])&                     &                     &                     &     (0.379)         \\
 [1em]
---times             &                     &                     &                     &      -0.118         \\
-teamwork-intensive share&                     &                     &                     &     (1.270)         \\
+\hspace*{1em}$\times$~teamwork-intensive~share&                     &                     &                     &      -0.118         \\
+\hspace*{1em}([0,1])&                     &                     &                     &     (1.270)         \\
 \hline

### 2020-07-01 text/regression.tex
BUGFIX: Use May employment numbers (was April before)

@@
 \hline
-Customer-facing~workers&      -0.293\sym{**} &                     &                     &                     \\
-\hspace*{1em}(share, [0,1])&     (0.138)         &                     &                     &                     \\
+Customer-facing~workers&      -0.300\sym{**} &                     &                     &                     \\
+\hspace*{1em}(share, [0,1])&     (0.116)         &                     &                     &                     \\
 [1em]
-\hspace*{1em}of~which~face-to-face&                     &      -0.409\sym{**} &      -0.453\sym{***}&       0.066         \\
-\hspace*{1em}intensive (share, [0,1])&                     &     (0.158)         &     (0.142)         &     (0.155)         \\
+\hspace*{1em}of~which~face-to-face&                     &      -0.347\sym{**} &      -0.397\sym{***}&       0.070         \\
+\hspace*{1em}intensive (share, [0,1])&                     &     (0.131)         &     (0.111)         &     (0.130)         \\
 [1em]
-Teamwork-intensive~workers&       0.677\sym{***}&                     &                     &                     \\
-\hspace*{1em}(share, [0,1])&     (0.156)         &                     &                     &                     \\
+Teamwork-intensive~workers&       0.462\sym{***}&                     &                     &                     \\
+\hspace*{1em}(share, [0,1])&     (0.132)         &                     &                     &                     \\
 [1em]
-\hspace*{1em}of~which~face-to-face&                     &       0.107         &       0.343         &       0.400         \\
-\hspace*{1em}intensive (share, [0,1])&                     &     (0.531)         &     (0.486)         &     (0.760)         \\
+\hspace*{1em}of~which~face-to-face&                     &      -0.282         &      -0.042         &       0.315         \\
+\hspace*{1em}intensive (share, [0,1])&                     &     (0.529)         &     (0.445)         &     (0.702)         \\
 [1em]
-Presence-intensive~workers&       0.224\sym{**} &       0.079         &      -0.053         &       0.005         \\
-\hspace*{1em}(share, [0,1])&     (0.111)         &     (0.120)         &     (0.128)         &     (0.107)         \\
+Presence-intensive~workers&       0.148         &       0.077         &      -0.071         &      -0.025         \\
+\hspace*{1em}(share, [0,1])&     (0.098)         &     (0.105)         &     (0.097)         &     (0.082)         \\
 [1em]
-Change~in~number~of &                     &                     &       0.188\sym{***}&      -0.084         \\
-\hspace*{1em}monthly visits (log)&                     &                     &     (0.059)         &     (0.122)         \\
+Change~in~number~of &                     &                     &       0.202\sym{***}&      -0.099         \\
+\hspace*{1em}monthly visits (log)&                     &                     &     (0.057)         &     (0.096)         \\
 [1em]
-\hspace*{1em}$\times$~customer-facing~share&                     &                     &                     &       1.105\sym{***}\\
-\hspace*{1em}([0,1])&                     &                     &                     &     (0.379)         \\
+\hspace*{1em}$\times$~customer-facing~share&                     &                     &                     &       1.006\sym{***}\\
+\hspace*{1em}([0,1])&                     &                     &                     &     (0.319)         \\
 [1em]
-\hspace*{1em}$\times$~teamwork-intensive~share&                     &                     &                     &      -0.118         \\
-\hspace*{1em}([0,1])&                     &                     &                     &     (1.270)         \\
+\hspace*{1em}$\times$~teamwork-intensive~share&                     &                     &                     &       0.351         \\
+\hspace*{1em}([0,1])&                     &                     &                     &     (1.097)         \\
 \hline
 Observations        &          79         &          79         &          78         &          78         \\
-\(R^{2}\)           &       0.245         &       0.183         &       0.307         &       0.452         \\
+\(R^{2}\)           &       0.221         &       0.200         &       0.383         &       0.555         \\
 \hline\hline

### 2020-07-01 text/regression.tex
Use April for both CES employment and SafeGraph visits
Results are essentially identical. Resolves #13

@@
 \hline
-Customer-facing~workers&      -0.300\sym{**} &                     &                     &                     \\
-\hspace*{1em}(share, [0,1])&     (0.116)         &                     &                     &                     \\
+Customer-facing~workers&      -0.311\sym{**} &                     &                     &                     \\
+\hspace*{1em}(share, [0,1])&     (0.142)         &                     &                     &                     \\
 [1em]
-\hspace*{1em}of~which~face-to-face&                     &      -0.347\sym{**} &      -0.397\sym{***}&       0.070         \\
-\hspace*{1em}intensive (share, [0,1])&                     &     (0.131)         &     (0.111)         &     (0.130)         \\
+\hspace*{1em}of~which~face-to-face&                     &      -0.418\sym{**} &      -0.463\sym{***}&       0.012         \\
+\hspace*{1em}intensive (share, [0,1])&                     &     (0.164)         &     (0.152)         &     (0.173)         \\
 [1em]
-Teamwork-intensive~workers&       0.462\sym{***}&                     &                     &                     \\
-\hspace*{1em}(share, [0,1])&     (0.132)         &                     &                     &                     \\
+Teamwork-intensive~workers&       0.676\sym{***}&                     &                     &                     \\
+\hspace*{1em}(share, [0,1])&     (0.160)         &                     &                     &                     \\
 [1em]
-\hspace*{1em}of~which~face-to-face&                     &      -0.282         &      -0.042         &       0.315         \\
-\hspace*{1em}intensive (share, [0,1])&                     &     (0.529)         &     (0.445)         &     (0.702)         \\
+\hspace*{1em}of~which~face-to-face&                     &       0.024         &       0.254         &       0.600         \\
+\hspace*{1em}intensive (share, [0,1])&                     &     (0.563)         &     (0.532)         &     (0.839)         \\
 [1em]
-Presence-intensive~workers&       0.148         &       0.077         &      -0.071         &      -0.025         \\
-\hspace*{1em}(share, [0,1])&     (0.098)         &     (0.105)         &     (0.097)         &     (0.082)         \\
+Presence-intensive~workers&       0.218\sym{*}  &       0.079         &      -0.051         &      -0.005         \\
+\hspace*{1em}(share, [0,1])&     (0.113)         &     (0.125)         &     (0.136)         &     (0.113)         \\
 [1em]
-Change~in~number~of &                     &                     &       0.202\sym{***}&      -0.099         \\
-\hspace*{1em}monthly visits (log)&                     &                     &     (0.057)         &     (0.096)         \\
+Change~in~number~of &                     &                     &       0.185\sym{***}&      -0.119         \\
+\hspace*{1em}monthly visits (log)&                     &                     &     (0.063)         &     (0.131)         \\
 [1em]
-\hspace*{1em}$\times$~customer-facing~share&                     &                     &                     &       1.006\sym{***}\\
-\hspace*{1em}([0,1])&                     &                     &                     &     (0.319)         \\
+\hspace*{1em}$\times$~customer-facing~share&                     &                     &                     &       1.021\sym{**} \\
+\hspace*{1em}([0,1])&                     &                     &                     &     (0.447)         \\
 [1em]
-\hspace*{1em}$\times$~teamwork-intensive~share&                     &                     &                     &       0.351         \\
-\hspace*{1em}([0,1])&                     &                     &                     &     (1.097)         \\
+\hspace*{1em}$\times$~teamwork-intensive~share&                     &                     &                     &       0.332         \\
+\hspace*{1em}([0,1])&                     &                     &                     &     (1.500)         \\
 \hline
 Observations        &          79         &          79         &          78         &          78         \\
-\(R^{2}\)           &       0.221         &       0.200         &       0.383         &       0.555         \\
+\(R^{2}\)           &       0.245         &       0.187         &       0.302         &       0.435         \\
 \hline\hline

### 2020-07-02 text/regression.tex
Remove column 1 from regression
Re #14

--- 2020-07-01 text/regression.tex
@@
 {\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}\begin{tabular}{l*{4}{D{.}{.}{-1}}}\hline\hline
-                    &\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
-                    &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} \\
+                    &\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}\\
+                    &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} \\
 \hline
-Customer-facing~workers&      -0.300\sym{**} &                     &                     &                     \\
-\hspace*{1em}(share, [0,1])&     (0.116)         &                     &                     &                     \\
+Customer-facing~workers&      -0.418\sym{**} &      -0.463\sym{***}&       0.012         \\
+\hspace*{1em}(share, [0,1])&     (0.164)         &     (0.152)         &     (0.173)         \\
 [1em]
-\hspace*{1em}of~which~face-to-face&                     &      -0.347\sym{**} &      -0.397\sym{***}&       0.070         \\
-\hspace*{1em}intensive (share, [0,1])&                     &     (0.131)         &     (0.111)         &     (0.130)         \\
+Teamwork-intensive~workers&       0.024         &       0.254         &       0.600         \\
+\hspace*{1em}(share, [0,1])&     (0.563)         &     (0.532)         &     (0.839)         \\
 [1em]
-Teamwork-intensive~workers&       0.462\sym{***}&                     &                     &                     \\
-\hspace*{1em}(share, [0,1])&     (0.132)         &                     &                     &                     \\
+Presence-intensive~workers&       0.079         &      -0.051         &      -0.005         \\
+\hspace*{1em}(share, [0,1])&     (0.125)         &     (0.136)         &     (0.113)         \\
 [1em]
-\hspace*{1em}of~which~face-to-face&                     &      -0.282         &      -0.042         &       0.315         \\
-\hspace*{1em}intensive (share, [0,1])&                     &     (0.529)         &     (0.445)         &     (0.702)         \\
+Change~in~number~of &                     &       0.185\sym{***}&      -0.119         \\
+\hspace*{1em}monthly visits (log)&                     &     (0.063)         &     (0.131)         \\
 [1em]
-Presence-intensive~workers&       0.148         &       0.077         &      -0.071         &      -0.025         \\
-\hspace*{1em}(share, [0,1])&     (0.098)         &     (0.105)         &     (0.097)         &     (0.082)         \\
+\hspace*{1em}$\times$~customer-facing~share&                     &                     &       1.021\sym{**} \\
+\hspace*{1em}([0,1])&                     &                     &     (0.447)         \\
 [1em]
-Change~in~number~of &                     &                     &       0.202\sym{***}&      -0.099         \\
-\hspace*{1em}monthly visits (log)&                     &                     &     (0.057)         &     (0.096)         \\
-[1em]
-\hspace*{1em}$\times$~customer-facing~share&                     &                     &                     &       1.006\sym{***}\\
-\hspace*{1em}([0,1])&                     &                     &                     &     (0.319)         \\
-[1em]
-\hspace*{1em}$\times$~teamwork-intensive~share&                     &                     &                     &       0.351         \\
-\hspace*{1em}([0,1])&                     &                     &                     &     (1.097)         \\
+\hspace*{1em}$\times$~teamwork-intensive~share&                     &                     &       0.332         \\
+\hspace*{1em}([0,1])&                     &                     &     (1.500)         \\
 \hline
-Observations        &          79         &          79         &          78         &          78         \\
-\(R^{2}\)           &       0.221         &       0.200         &       0.383         &       0.555         \\
+Observations        &          79         &          78         &          78         \\
+\(R^{2}\)           &       0.187         &       0.302         &       0.435         \\
 \hline\hline

### 2020-07-02 text/abstract.tex
Pull most recent version from OverLeaf

@@
 Here we provide theory-based measures of the reliance of U.S. businesses on human interaction, detailed by industry and geographic location.
-We find that 49 million workers work in occupations that rely heavily on face-to-face communication or require close physical proximity to other workers.
-Our model suggests that when businesses are forced to reduce worker contacts by half, they need a 12 percent wage subsidy to compensate for the disruption in communication.
-Retail, hotels and restaurants, arts and entertainment and schools are the most affected sectors.
-Our results can help target fiscal assistance to businesses that are most disrupted by social distancing.
+We find that, before the pandemic hit, 35 million workers worked in occupations that rely heavily on face-to-face communication or require close physical proximity to other workers.
+Many of these workers lost their jobs since.
+Consistently with our model, employment losses have been largest in sectors that rely heavily on customer contact and where these contacts dropped the most: retail, hotels and restaurants, arts and entertainment and schools.
+Our results can help quantify the economic costs of social distancing.

### 2020-07-02 text/content.tex
Pull most recent version from OverLeaf

@@
 \section*{Introduction}
+
 Social distancing measures are effective non-pharmaceutical interventions against the rapid spread of epidemics \cite{Bootsma2007-ww,Markel2007-ad,Hatchett2007-gc,Wilder-Smith2020-jj}.
-Many countries have implemented or are considering measures such as school closures, prohibition of large gatherings and restrictions on non-essential stores and transportation to slow down the spread of the 2019--20 coronavirus pandemic \cite{Anderson2020-qk,Cohen2020-jw,Thompson2020-lc,noauthor_2020-xi}.
+Many countries have implemented measures such as school closures, prohibition of large gatherings and restrictions on non-essential stores and transportation to slow down the spread of the 2019--20 coronavirus pandemic \cite{Anderson2020-qk,Cohen2020-jw,Thompson2020-lc,noauthor_2020-xi}.
 What are the economic effects of such social distancing interventions?
@@
 For this question, past data may be less relevant, as the importance of face-to-face communication has increased steadily in the last 100 years through urbanization \cite{Henderson2010-mv,Henderson2002-ji} and specialization increased in business services as well \cite{Herrendorf2014-jx,Duarte2019-kc}.
+Even if advances in information and communication technology made it increasingly possible to communicate with co-workers and customers without the need for physical face-to-face interactions, personal contacts are still inevitable in some industries.
+During the 2020 lockdown in the Netherlands only 31 percent of workers in the retail sector, 27 percent of the workers in the catering sector and 31 percent of the workers in the construction sector reported working from home \cite{von2020labour}.
 
@@
 This division of labor reduces production costs but requires frequent contact between workers.
-In the model, the number of contacts per worker is the most frequent in high-population-density areas in businesses where the division of labor is important.
+In the model, the number of contacts per worker is the most frequent in businesses where the division of labor is important.
 When face-to-face interaction is limited, these are exactly the businesses that suffer the most.
 
-To measure business disruptions from social distancing, we turn to recent data on the task descriptions of each occupation \cite{National_Center_for_ONET_Development2020-wj} and the precise geographic location of non-farm businesses in the U.S.
-\cite{CBP}.
-We construct three groups of occupations and study their distribution in space.
+To measure business disruptions from social distancing, we turn to recent data on the task descriptions of each occupation \cite{National_Center_for_ONET_Development2020-wj}, the precise geographic location of non-farm businesses in the U.S.
+\cite{CBP}, and customer mobility patterns \cite{SafeGraph2020-gn}.
+We construct three groups of occupations.
 First, some occupations require face-to-face communication several times a week with other workers.
 Examples of these \emph{teamwork-intensive} occupations include maintenance, personal care related occupations and health care professionals.
-Other occupations require frequent contact with customers.
-Counselors, social workers and salespersons are examples of such \emph{customer-facing} occupations.
+Other occupations require frequent face-to-face contact with customers.
+Retail salespersons, social workers and waiters and waitresses are examples of such \emph{customer-facing} occupations.
 The third group of workers may need to be in physical proximity of one another even if they do not communicate, for example, to operate machinery or access key resources.
 Examples of such occupations requiring \emph{physical presence} are drivers and machine operators, especially in mining and water transport, where crammed working environments are common.
+With our occupation level measures, we aim to capture the jobs that can be performed less efficiently from home.
+As O*NET measures the type of activities that are performed by the worker during normal times, we validate our indexes by using the American Time Use Survey (ATUS) \cite{ATUS}.
+The survey directly asks about the possibility of working from home.
 
-The spatial distribution of employment matters because face-to-face interactions are more frequent in dense cities \cite{Charlot2004-zr,Tian2019-wq}.
-So any social distancing intervention imposes disproportionately more limitation on urban sectors.
-We use our theory-motivated measures to estimate which sectors and which locations will be particularly hurt by social distancing.
+To study how the patterns of interaction have changed in the U.S.
+during the Covid-19 pandemic, we use customer mobility data from SafeGraph \cite{SafeGraph2020-gn}.
+This dataset measures the number of visits to a business in a given month, as captured from several cell phone apps and made available to researchers in an anonymized form.
+???????
 
@@
 The benefit of a larger team is better specialization.
+Law firms, management teams, and IT service firms are prime examples of businesses where intensive communication leads to narrow specialization \cite{Garicano2009-jv}.
 Second, communication may involve the customer (panel B).
 The benefit of more frequent interaction with the customer is a product or service that is better suited to their needs.
-Third, workers may need access to a key physical resource, such as a machine, vehicle or an oil well (panel C).
+Restaurants, beauty salons, personal and social services require such frequent interaction exactly because their service is so customized.
+Third, workers may need access to a key physical resource (panel C).
 In this case, even if they do not communicate, they may be subject to social distancing measures.
+For example, operators of machines, vehicle drivers or workers on an oil rig are all very much tied to a key resource to do their job.
 The key assumption behind all three interpretations is that frequent interaction increases productivity, whether happening between workers, between workers and customers, or between workers and machines.
@@
 
-\subsection*{The cost of communication}
-Businesses may differ in $\chi$, how important communication is in their production process.
-Another source of heterogeneity is the cost of communication between workers, which we specify further as follows.
+\subsection*{Social distancing}
 
-When workers meet face to face, communication costs depend inversely on the population density in the neighborhood of the firm, $\tau=d^{-\varepsilon}$ with $\varepsilon>0$.
-This captures the Marshallian externality of knowledge spillovers \cite{Marshall1920-ps}, which happen more easily in densely populated areas \cite{Charlot2004-zr,Rossi-Hansberg2007-tm,Ioannides2008-bs,Tian2019-wq}.
-Contacts will be more frequent in dense areas,
-\begin{equation}\label{communication}
-	n^*(d) = d^{\varepsilon(1-\chi)}.
+We study the effect of social distancing, which reduces the number of face-to-face contacts to some exogenous value $N$.
+This may be mandated by government orders to close certain places of business or stay at home.
+But it can also be the result of voluntary social distancing in response to the risk of infection.
+
+The optimal number of contacts without social distancing is given by Eq \eqref{nstar}.
+Firms with $n^*>N$ are limited by social distancing.
+Without moving communication online, their unit cost will increase to $c' = N \tau + N^{-\gamma}/\gamma$, which is greater than the optimal cost,
+\begin{equation}\label{socdist}
+\frac{c'}{c} 
+	= \chi \frac{N}{n^*} + (1-\chi) \left(\frac{N}{n^*}\right)^{-\gamma}>1.
 \end{equation}
-The unit cost of production is
-\begin{equation}\label{cost2}
-c(d) = d^{-\varepsilon\chi}/\chi.
-\end{equation}
-Firms in dense areas face lower unit costs \cite{Ciccone1996-gu}, but this agglomeration benefit may be offset by higher wages and land rents in places with high population density \cite{Eberts1982-zf,Madden1985-pq,Combes2019-ud}.
-In spatial equilibrium (not modeled here), firms with high communication needs will choose to locate in high-density areas \cite{Tian2019-wq}.
-
-\subsection*{Social distancing measures}
-We study the effect of a social distancing intervention that puts an upper limit $N$ on the number of face-to-face contacts.
-Firms can mitigate the disruption from this measure by moving communication online, but this is more costly per contact than face-to-face communication.
-
-The optimal number of contacts without social distancing is given by Eq \eqref{communication}.
-Firms with $n^*>N$ are limited by social distancing.
-Without moving communication online, their unit cost will increase to $c' = N d^{-\varepsilon} + N^{-\gamma}/\gamma$, which is greater than the optimal cost,
-\begin{equation}\label{socdist}
-\frac{c'(d)}{c(d)} 
-	= \chi \frac{N}{n^*(d)} + (1-\chi) \left(\frac{N}{n^*(d)}\right)^{-\gamma}>1.
-\end{equation}
-The first term of the weighted average is less than one, representing a reduction in communication costs once the number of contacts is limited.
+The first term of the weighted average is less than one, representing a reduction in communication costs once the number of contacts declines.
 The second term is greater than one due to the fact that every worker has to complete a wider range of tasks than before, and they lose the benefit of specialization.
@@
 
-If the firm chooses to use telecommunication, the cost per contact will be $T>d^{\varepsilon}$ (otherwise the firm would have used telecommunication before).
-The proportional increase in production costs in this case is given by
-\begin{equation}\label{telco}
-\frac{c''(d)}{c(d)} 
-	= T^\chi d^{\varepsilon \chi}
-	>1.
-\end{equation}
-In both cases, the cost increase is highest for communication-intensive firms (large $\gamma$ and $\chi$) and those operating in a high-density area (high $d$ and hence high $n^*$).
-
-Fig \ref{fig2} displays the ratio of production costs under social distancing to the optimal production costs as a function of density.
-Firms in low-density areas are unaffected by social distancing since they do not have many contacts anyway.
-Those in intermediate-density areas would suffer less of a cost increase by switching to telecommunication.
-Firms in the highest-density areas will stick to face-to-face communication, which is still the more efficient form of communication despite restrictions.
-However, they will suffer the greatest cost increase.
-
-\begin{figure}[!h]
-\plos{\centering\input{fig2-input}}
-
-\caption{{\bf Both social distancing and telecommunication hurt firms in dense areas more.}
-See Eq \eqref{socdist} and Eq \eqref{telco} for the relative production costs under the two interventions.}
-\label{fig2}
-\end{figure}
-
 \section*{Data and methodology}
-To estimate the potential disruptions from social distancing, we need a measure of the importance of worker interaction (corresponding to $\chi$ in the model) and its cost (captured by population density $d$).
+To estimate the potential disruptions from social distancing, we need a measure of the importance of worker interaction (corresponding to $\chi$ in the model) and its change (captured by the ratio $N/n^*$).
 
@@
 As social distancing measures only limit personal communication, for communication indexes, we require that the necessary face-to-face communication happens at least several times a week.
-In teamwork, face-to-face meetings can often be substituted by more structured communication, for which working from home is not as disruptive.
-To allow for this possibility, we only classify occupations as teamwork-intensive where both emails and letters and memos are less frequent forms of communication than face-to-face meetings.
+Face-to-face meetings can often be substituted by more structured communication, for which working from home is not as disruptive.
+To allow for this possibility, we only classify occupations as teamwork-intensive or customer-facing where both emails and letters and memos are less frequent forms of communication than face-to-face meetings.
 This excludes most managers and certain business services.
@@
 \begin{table}[!ht]
-%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \caption{
 {\bf Definition of social distancing indexes.}}
-\begin{tabular}{|l|l|l|}
+\begin{tabular}{|l+l|l|}
 \hline
@@
 &  Performing for or Working Directly with the Public & discussions \\
-& Assisting and Caring for Others & several \\
-& Provide Consultation and Advice to Others & times a week\\
-& Establishing and Maintaining Interpersonal Relationships &\\
+& Assisting and Caring for Others & several times a week \\
+& Provide Consultation and Advice to Others & \& more often than\\
+& Establishing and Maintaining Interpersonal Relationships & emails, letters, memos \\
 \hline
@@
 \label{table1}
-%\end{adjustwidth}
+\end{adjustwidth}
 \end{table}
@@
 
-As a next step, we calculate for each sector the share of workers whose job requires a high level of teamwork, customer contact and physical presence. 
+With our occupation-level measures, we aim to capture the type of activities that require frequent face-to-face contact.
+Our assumption is that these activities cannot be effectively done from home.
+To validate this assumption, we use data from the American Time Use Survey (ATUS) \cite{ATUS}, which directly asks the workers whether they \emph{can} work from home.
+Fig.
+\ref{customer_validation} plots our customer-intensity measure, for each occupation, against the share of workers who reported in ATUS that they can work from home (dark filled circles).
+Indeed, most customer-facing occupations have very few workers who can work from home.
+The pattern is different if we look at occupations that rely more on email, letters, and memos for customer communication (light hollow circles).
+The majority of these workers can work from home.
+Interestingly, for each degree of working from home (horizontal axis), there is sufficient variation in the importance of customer contact (vertical axis).
+The same patterns can be observed for teamwork-intensive occupations (Fig.
+\ref{teamwork_validation}).
+This makes use conclude that dropping occupations primarily relying on email, letters and memos is sufficient to control for the potential to work from home.
+
+\begin{figure}[!h]
+\plos{\includegraphics[width=0.7\linewidth]{customer_atus_validation.pdf}}
+
+\caption{{\bf Workers in customer-facing occupations with face-to-face interaction can rarely work from home.}
+Filled circles represent the occupations where face-to-face contacts are more important than emails and memos.
+Hollow circles represent the occupations where emails and memos are more important than face-to-face contacts.
+The indexes are constructed as explained in main text.
+}
+\label{customer_validation}
+\end{figure}
+
+\begin{figure}[!h]
+\plos{\includegraphics[width=0.7\linewidth]{teamwork_atus_validation.pdf}}
+
+\caption{{\bf Workers in teamwork-intensive occupations with face-to-face interaction can rarely work from home.}
+Filled circles represent the occupations where face-to-face contacts are more important than emails and memos.
+Hollow circles represent the occupations where emails and memos are more important than face-to-face contacts.
+The indexes are constructed as explained in main text.
+}
+\label{teamwork_validation}
+\end{figure}
+
+With our validated occupation measures in hand, our next step is to calculate for each sector the share of workers whose job requires a high level of teamwork, customer contact, and physical presence.
 We use the same sectoral breakdown as the Current Employment Statistics (CES) \cite{CES}.
-As all the indexes are an absolute value running from 0 to 100, we use 62.5 as a cutoff to define a job to be teamwork-intensive, customers contact-intensive or job that require physical presence from the worker.
+As all the indexes are an absolute value running from 0 to 100, we use 62.5 as a cutoff to define a job to be teamwork-intensive, customers contact-intensive, or job that requires physical presence from the worker.
 The occupation structure of the industries are retrieved from the official industry-occupation matrix \cite{employment-matrix}, we use the employment statistics by occupation-industry for February 2020.
@@
 
-To measure the heterogeneity in the cost of communication, we measure population density in the neighborhood of businesses.
-The assumption in the model is that communication costs are lower in dense areas.
-This is consistent with the fact that communication-intensive sectors such as business services and advertising, together with central administrative offices of production firms tend to be concentrated in high-density areas \cite{Aarland2007-dh}.
+To measure how the number of interactions has changed due to social distancing, we use data from SafeGraph \cite{SafeGraph2020-gn}, a data company that aggregates anonymized location data from numerous applications to provide insights about physical places.
+To enhance privacy, SafeGraph excludes census block group information if fewer than five devices visited an establishment in a month from a given census block group.
 
-The location of sectors comes from the County Business Patterns (CBP) data for 2017 \cite{CBP}.
+We use the Monthly Patterns file that captures the number of visits by mobile devices in the sample to more than 4 million points of interest (POIs) in each month.
+Each POI is assigned a specific address, including a ZIP code, and a 6-digit NAICS code.
+Because the pandemic hit different regions of the U.S.
+at different times, we use both the industry and the regional variation of customer mobility data.
+We aggregate monthly visits by 3-digit NAICS code and ZIP code.
+This enables us to measure by how much, for example, visits to clothing stores have declined in downtown Manhattan.
+
+We measure the percentage change in the number of visits between February and May 2020.
+When the industry-ZIP cell received fewer than ten visits in either month or when visits data are missing in SafeGraph, we replace the change in visits with the average of the ZIP code.
+
+To validate the customer mobility data, we check the location of sectors in the County Business Patterns (CBP) data for 2017 \cite{CBP}.
 For a finer spatial resolution, we use the data tabulated by ZIP-Code Tabulation Areas.
 The CBP lists the number of establishments of a certain size for each ZIP-code and NAICS industry code.
+We estimate the employment of each industry in each ZIP code to be able to compute employment-weighted national averages of our statistics of interest.
+
 Because establishment sizes are given in bins (e.g., 1--4 employees), we take the midpoint of each bin as our estimated employment (e.g., 2.5 employees).
@@
 
-To understand the heterogeneity across regions, we average the share of workers in teamwork-intensive, customer-facing and physical presence occupations across industries active in each ZIP code.
-For each of the three occupation groups, let $\xi_{og}$ denote the indicator whether occupation $o$ belongs to group $g$.
-The industry share of workers in the occupation group is given by $\sum_o s_{io}\xi_{og}$.
-We compute the regional share of the occupation group as an employment-weighted average across industries, $\sum_i l_{ir}\sum_o s_{io}\xi_{og}/\sum_i l_{ir}$, where $l_{ir}$ is the estimated employment of industry $i$ in region (ZIP code) $r$.
-Because we only have industry but not occupation data by location, we have assumed that the occupation distribution within the sector, $s_{io}$, does not vary across locations.
-The fact that the CBP tabulates employment by establishments rather than firms makes this a good approximation.
-For example, a sporting good producer may also have an administrative office and a retail store in different locations, but these will be classified in their respective NAICS sectors rather than in sporting good manufacturing.
-
-We use population density to measure how locations differ in the costs of communication.
-We also experimented with using employment densities instead of population densities.
-Results were very similar, as the two measures are highly correlated with the exception of very high employment-density urban centers where population is more sparse \cite{Heblich2017-lb}.
-
 \subsection*{Counterfactual calculations}
-To gauge the magnitude of the effect of social distancing, we calibrate the parameters of the model and compute the effect of a policy that limits the number of worker contacts.
+To gauge the magnitude of the effect of social distancing, we compute the effect of the decline in the number of customer-worker contacts.
 At the same time, we let the government introduce a proportional wage subsidy $\lambda$ to help offset the costs from lower interaction.
 With this subsidy, the cost of labor will be $(1-\lambda)$.
-We ask what level of $\lambda$ would compensate businesses for the communication disruption caused by social distancing.
-Using the cost change in Eq \ref{socdist}, we can express
+
+We ask what level of $\lambda$ would exactly compensate businesses for the communication disruption caused by social distancing.
+When interactions decrease, $N<n^*$, production costs increase.
+We compute the subsidy $\lambda$, which, when given to every worker, would exactly offset the cost increase.
+This way the business would not have to fire any of its workers.
+The goal of this exercise is not to evaluate any particular employment support policy, but to get a sense of the magnitude of business disruptions.
+
+Using the cost change in Eq \ref{socdist}, we can express the compensating labor subsidy of industry $i$ in region $r$ as
 \begin{equation}\label{subsidy}
     \lambda_{ir} = 1 -
-        \frac{1-\chi_i}{1-\chi_i N/n_{ir}^*}
+        \frac{1-\chi_i}{1-\chi_i N_{ir}/n_{ir}^*}
         \left(
-        \frac{N}{n_{ir}^*}
+        \frac{N_{ir}}{n_{ir}^*}
         \right)^{\gamma_i}>0.
 \end{equation}
-The compensating wage subsidy increases in the importance of communication $\chi_i$ and the optimal number of contacts $n^*_{ir}$, and decreases in the number of allowed contacts $N$.
-The subscripts note that communication share is industry specific and the optimal number of contacts is both industry and region specific.
-
-We calibrate the upper limit on personal contacts $N$ such that the overall number of contacts in the economy, when averaged across ZIP codes and industries, is reduced by half, $\sum_{i,r}l_{ir}\min\{N,n_{ir}^*\} = 0.5\sum_{i,r}l_{ir}n_{ir}^*$.
-Due to the inherent nonlinearity of the model, other interventions will have different effects.
+We calibrate $n_{ir}^*$ to match the number of customer visits to establishments of industry $i$ in ZIP-code $r$ in February 2020, assuming that these visits were optimal before the pandemic hit the U.S.
+The new number of visits, $N_{it}$ will be calibrated to the number of customer visits in May 2020.
+The compensating wage subsidy increases in the importance of communication $\chi_i$ and decreases in the change in cotacts $N_{ir}/n^*_{ir}$.
+The subscripts note that communication share is industry specific and the change in contacts is both industry and region specific.
 
 To calibrate the importance of communication $\chi_i$, note that it is the cost share of communication, and can be correspondingly calibrated to the employment share of communication-intensive occupations in industry $i$.
-Here we take all occupations that are either teamwork intensive or customer facing.
-
-Population density in region $r$ can be measured directly in the data, as explained above.
-The only remaining parameter to calibrate is the elasticity of the communication externality $\varepsilon$.
-We rely on previous estimates of agglomeration effects that capture the elasticity of total factor productivity with respect to population density \cite{Ciccone1996-gu}.
-In our model, the elasticity of unit costs (which can be construed as the inverse of productivity) with respect to density is $-\varepsilon\chi$ (Eq \eqref{cost2}).
-We calibrate $\varepsilon=0.02$ so that, across all ZIP codes and industries, a regression of log model-implied productivity ($\varepsilon\chi_i\ln d_r$) on log population density $\ln d_r$ yields an elasticity of 0.04 \cite[page 60]{Ciccone1996-gu}.
-
-Given these parameter values, we compute the compensating wage subsidy for each industry in each ZIP code using Eq \ref{subsidy}.
+We then compute the compensating wage subsidy for each industry in each ZIP code using Eq \ref{subsidy}.
 We report employment-weighted averages of this across sectors and across locations.
@@
 Table \ref{table2} displays the top five and the bottom five industries by 2-digit NAICS industries as sorted by the percentage of workers in communication-intensive occupations, excluding hospitals and clinics.
-Across industries, retail trade, accommodation and food services, arts, entertainment, and recreation, other services and educational services have the highest share of communication-intensive workers, exceeding 35 percent.
-Transportation, production, construction and agricultural industries are less reliant on face-to-face communication.
+Across industries, retail trade, accommodation and food services, arts, entertainment, and recreation, other services and administrative and support and waste management and remediation services have the highest share of communication-intensive workers, exceeding 35 percent.
+Information, transportation, production, professional, scientific, and technical Services and agricultural industries are less reliant on face-to-face communication.
 This heterogeneity across industries is important to understand the effect of social distancing measures.
@@
 \caption{
-{\bf Retail, professional services, finance and restaurants are the most communication intensive.}}
-\begin{tabular}{|l|c|c|c|c|}
+{\bf Retail, accommodation and restaurants are the most communication intensive.}}
+\begin{tabular}{|l+c|c|c+c|}
 \hline
@@
 \\ \thickhline
-Retail trade &13&67&68&5\\
-Accommodation \& food services &8&50&51&1\\
-Arts, Entertainment, and Recreation &12&40&42&2\\
-Other Services (except Public Admin.) &12&38&41&12\\
-Educational Services &15&35&37&1\\
+Retail trade &13&65&66&4\\
+Accommodation \& food services &9&49&51&1\\
+Arts, Entertainment, and Recreation &12&37&40&2\\
+Other Services (except Public Admin.) &12&28&30&13\\
+Admin. \& Support \& Waste Manag.  &	17&	24&	7&	27\\
+\& Remed. Serv. &&&& \\
 ...&&&&\\
-Wholesale Trade &8&16&20&12\\
-Transportation and Warehousing  &8&10&16&32\\
-Manufacturing &7&6&11&10\\
-Construction &15&5&18&28\\
-Agri., forestry, fishing \& hunting &4&4&7&23\\
+Information&	6&	13&	15&	9\\
+Transportation and Warehousing&	8&	8&	14&	33\\
+Prof., Scient., and Technical Serv.&	5&	10&	12&	1\\
+Manufacturing&	7&	5&	9&	10\\
+Agri., forestry, fishing \& hunting &	4&	1&	4&	23\\
+
  \thickhline
@@
 
-Fig \ref{fig4} plots the share of workers in the three affected occupation groups across ZIP codes by population density.
-Customer-facing occupations are overrepresented in dense areas.
-In the highest population density ZIP codes, 43 percent of workers are employed in customer-facing occupations.
-Teamwork-intensive occupations are broadly distributed in space.
+Table \ref{table4} reports the results of regressing the log change in industry employment between February and May 2020 on our social distancing indexes.
+Each regression is estimated with unweighted ordinary least squares.
+Across the entire non-farm economy, employment has dropped by 13 percent (not seasonally adjusted) \cite{CES}.
 
-\begin{figure}[!h]
-\plos{\includegraphics[width=0.7\linewidth]{fig4.pdf}}
-
-\caption{{\bf Urban areas employ more workers in customer-facing occupations, less in occupations requiring physical presence.}
-Locally weighted polynomial regression of average share of teamwork-intensive occupations, customer-facing occupations and occupations requiring physical presence across sectors within the ZIP code (bandwidth $=0.5$).}
-\label{fig4}
-\end{figure}
-
-In the calibrated model, a social distancing policy that puts a cap on interactions per worker such that the total number of interactions drops by half nationwide is compensated a 12.2 percent wage subsidy.
-The distribution of the compensating wage subsidy is, however, unequal over space and across industries.
-New York City, with a population density about 20 times the average U.S. city, would require a 13.3 percent wage subsidy. 
-By contrast, the compensating wage subsidy in agriculture, transportation and manufacturing would be less than 6 percent (Table \ref{table3}).
+As Column 1 shows, the drop was larger in industries with a larger share of customer-facing workers.
+There is no significant correlation between the share of workers with teamwork-intensive jobs or the share of workers requiring physical presence to do their work and employment losses.
+In Column 2, we control for the change in log customer visits.
+Indeed, changes in customer visits are positively correlated with changes in employment (both dropping for most of our industries).
+In Column 3, we introduce interactions with the change in log customer visits (as a proxy for $\ln (N/n^*)$) and the share of communication workers (as a proxy for $\chi$).
+As predicted by the model, the drop in customer visits has the largest effect on sectoral employment in sectors where the share of customer-facing workers is highest.
 
@@
 \caption{
-{\bf The five most affected sectors require more than 20 percent wage subsidy.}}
-\begin{tabular}{|l|c|c|}
+{\bf Employment decline was sharpest in customer-facing industries.}}
+\input{regression.tex}
+\begin{flushleft} Regression results of change in log industry employment between February and May 2020 estimated by ordinary least squares (unweighted).
+Explanatory variables in Column 1 are the shares of customer-facing, teamwork-intensive and presence-requiring workers.
+Column 2 controls for the change in log monthly visits to industry establishments.
+Column 3 interacts the change in visits with the share of face-to-face intensive  workers in the two occupation groups.
+Robust standard errors are reported in parentheses.
+$p$-values are denoted by asterisk: * $<.1$ ** $<.05$ *** $<.01$.
+Sample excludes hospitals, clinics, and government establishments, as well as farming and fishing which are not present in CBP.
+\end{flushleft}
+\label{table4}
+%\end{adjustwidth}
+\end{table}
+
+As we see from the regression results above, the largest decline in sectoral employment are in sectors where the share of customer-facing workers is highest.
+We hence use the share of customer-facing workers for the following analysis.
+
+In the calibrated model, the social distancing that took place between February and May 2020 would be compensated by a 39.9 percent wage subsidy.
+The distribution of the compensating wage subsidy is, however, unequal across industries.
+Retail trade, where customer visits practically ground to a halt, would require a 234 percent wage subsidy.
+By contrast, the compensating wage subsidy in agriculture, transportation and manufacturing would be less than 2 percent (Table \ref{table3}).
+
+\begin{table}[!ht]
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\caption{
+{\bf The five most affected sectors require more than 14 percent wage subsidy.}}
+\begin{tabular}{|l+c|c|}
 \hline
@@
 \\ \thickhline
-Retail Trade	&22.1	&15,659\\
-Accommodation and Food Services	&17.7	&14,379\\
-Arts, Entertainment, and Recreation	&15.1	&2,494\\
-Other Services (except Public Admin.)	&14.5	&5,939\\
-Educational Services	&13.8	&3,838\\
+Retail Trade	&234	&15,672\\
+Arts, Entertainment, and Recreation	&30.2	&2,472\\
+Accommodation and Food Services	&26.1	&14,394\\
+Educational Services	&22.2	&3,8328\\
+Other Services (except Public Admin.)	&14.5	&5,941\\
 ...&&\\
-Wholesale Trade	&7.7	&5,936\\
-Construction	&6.8	&7,646\\
-Transportation and Warehousing	&5.9	&5,523\\
-Manufacturing	&4.5	&12,861\\
-Agriculture, Forestry, Fishing and Hunting	&2.6	&55\\
+Mining          &2.0    &660\\
+Wholesale Trade	&1.8	&5,934\\
+Construction	&1.1	&7,639\\
+Manufacturing	&1.1	&12,852\\
+Agriculture, Forestry, Fishing and Hunting	&0.5	&55\\
 \hline
-{\bf Average} & {\bf 12.2} & {\bf 116,496}\\
+{\bf Average} & {\bf 39.9} & {\bf 116,441}\\
  \thickhline
@@
 \section*{Discussion and conclusions}
+
 The main cost of social distancing in our model is insufficient division of labor.
@@
 But social distancing measures also affect sectors where workers need to be in physical proximity of one another even if they do not communicate, for example, to operate machinery or access key resources.
-This is relevant in sectors like ``Mining, Quarrying, and Oil and Gas Extraction'' and ``Transportation'' while it is not relevant in sectors like ``Finance and Insurance'' and ``Professional, Scientific, and Technical Services.'' As can be seen from Fig \ref{fig4}, occupations requiring physical presence have the highest share in less dense areas where production and mining plants are located.
-(Farms are not included in the CBP.) The share of these occupations in the most dense areas is only 3 percent.
+This is relevant in sectors like ``Mining, Quarrying, and Oil and Gas Extraction'' and ``Transportation'' while it is not relevant in sectors like ``Finance and Insurance'' and ``Professional, Scientific, and Technical Services.''
 
@@
 Workers in this group are found to be the most vulnerable across a wide range of socio-economic measures \cite{Jin2020-tq,Mongey2020-qc}.
-We contribute to this work by (i) building a model to understand how social distancing measures affect the production, (ii) identifying three groups of occupations affected by social distancing and (iii) taking into account the disproportionate costs borne by urban sectors.
+We contribute to this work by (i) building a model to understand how social distancing measures affect the production, (ii) identifying three groups of occupations affected by social distancing and (iii) validating our model with customer visit and employment data.
 
@@
 Whenever productivity in any business drops, this shock can propagate to its buyers and suppliers.
-The aggregate consequences of the epidemic will hence be modulated by input-output linkages between sectors, regions and countries \cite{Caliendo2014-mr,Caselli2020-nf,Baldwin2020-wb}.
+The aggregate consequences of the epidemic will hence be modulated by input-output linkages between sectors, regions and countries \cite{Caliendo2014-mr,Caselli2020-nf,Baldwin2020-wb,Barrot2020-jf}.
 
@@
 
+\section*{Data Availability Statement}
+The mobility data used in this paper \cite{SafeGraph2020-gn} is confidential, but may be obtained free of charge for Covid-19-related research from the COVID-19 Consortium.
+Researchers interested in access to the data can apply at https://www.safegraph.com/covid-19-data-consortium.
+After signing a Data Agreement, access is granted within a few days.
+The authors will assist with any reasonable replication attempts for two years following publication.
+
+The code and all other data underlying our analysis are licensed for public use and will be made available on Zenodo.
+
 \section*{Supporting information}
@@
 {\bf Social distancing exposure by sector.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the industry.
-``Communucation share'' refers to the share of workers who are either teamwork-intensive or customer-facing.
+``Communication share'' refers to the share of workers who are either teamwork-intensive or customer-facing.
 ``Affected share'' refers to the share of workers in any of the three occupation groups.
@@
 {\bf Social distancing exposure by location.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the ZIP code.
-``Communucation share'' refers to the share of workers who are either teamwork-intensive or customer-facing.
+``Communication share'' refers to the share of workers who are either teamwork-intensive or customer-facing.
 ``Affected share'' refers to the share of workers in any of the three occupation groups.

### 2020-07-02 text/content.tex
Edit after proofreading

@@
 For this question, past data may be less relevant, as the importance of face-to-face communication has increased steadily in the last 100 years through urbanization \cite{Henderson2010-mv,Henderson2002-ji} and specialization increased in business services as well \cite{Herrendorf2014-jx,Duarte2019-kc}.
-Even if advances in information and communication technology made it increasingly possible to communicate with co-workers and customers without the need for physical face-to-face interactions, personal contacts are still inevitable in some industries.
-During the 2020 lockdown in the Netherlands only 31 percent of workers in the retail sector, 27 percent of the workers in the catering sector and 31 percent of the workers in the construction sector reported working from home \cite{von2020labour}.
+Even if advances in information and communication technology made it increasingly possible to communicate with co-workers and customers without the need for physical face-to-face interactions, personal contacts are still inevitable in some industries \cite{Dingel2020-lh,von2020labour}.
 
@@
 With our occupation level measures, we aim to capture the jobs that can be performed less efficiently from home.
-As O*NET measures the type of activities that are performed by the worker during normal times, we validate our indexes by using the American Time Use Survey (ATUS) \cite{ATUS}.
-The survey directly asks about the possibility of working from home.
+We validate our indexes by using the American Time Use Survey (ATUS) \cite{ATUS}, which directly asks about the possibility of working from home.
 
@@
 This dataset measures the number of visits to a business in a given month, as captured from several cell phone apps and made available to researchers in an anonymized form.
-???????
+We study how the reduced number of customer vists is correlated with changes in sectoral employment.
 
@@
 Firms with $n^*>N$ are limited by social distancing.
-Without moving communication online, their unit cost will increase to $c' = N \tau + N^{-\gamma}/\gamma$, which is greater than the optimal cost,
+Their unit cost will increase to $c' = N \tau + N^{-\gamma}/\gamma$, which is greater than the optimal cost,
 \begin{equation}\label{socdist}
@@
 Our assumption is that these activities cannot be effectively done from home.
-To validate this assumption, we use data from the American Time Use Survey (ATUS) \cite{ATUS}, which directly asks the workers whether they \emph{can} work from home.
-Fig.
-\ref{customer_validation} plots our customer-intensity measure, for each occupation, against the share of workers who reported in ATUS that they can work from home (dark filled circles).
+To validate this assumption, we use data from the American Time Use Survey (ATUS) \cite{ATUS}, which directly asks workers whether they \emph{can} work from home.
+Fig \ref{customer_validation} plots our customer-intensity measure, for each occupation, against the share of workers who reported in ATUS that they can work from home (dark filled circles).
 Indeed, most customer-facing occupations have very few workers who can work from home.
@@
 Interestingly, for each degree of working from home (horizontal axis), there is sufficient variation in the importance of customer contact (vertical axis).
-The same patterns can be observed for teamwork-intensive occupations (Fig.
-\ref{teamwork_validation}).
+The same patterns can be observed for teamwork-intensive occupations (Fig \ref{teamwork_validation}).
 This makes use conclude that dropping occupations primarily relying on email, letters and memos is sufficient to control for the potential to work from home.
@@
 The new number of visits, $N_{it}$ will be calibrated to the number of customer visits in May 2020.
-The compensating wage subsidy increases in the importance of communication $\chi_i$ and decreases in the change in cotacts $N_{ir}/n^*_{ir}$.
+The compensating wage subsidy increases in the importance of communication $\chi_i$ and decreases in the change in contacts $N_{ir}/n^*_{ir}$.
 The subscripts note that communication share is industry specific and the change in contacts is both industry and region specific.
@@
 \\ \thickhline
-Retail trade &13&65&66&4\\
-Accommodation \& food services &9&49&51&1\\
-Arts, Entertainment, and Recreation &12&37&40&2\\
-Other Services (except Public Admin.) &12&28&30&13\\
-Admin. \& Support \& Waste Manag.  &	17&	24&	7&	27\\
-\& Remed. Serv. &&&& \\
+Retail trade 						&13	&66	&67	&5\\
+Accommodation \& food services 		&8	&50	&51	&1\\
+Arts, Entertainment, and Recreation &12	&38	&40	&2\\
+Other Services (except Public Admin.)&12&30	&33	&12\\
+Admin. \& Support \& Waste Manag.  	&17	&24	&27	&7\\
 ...&&&&\\
-Information&	6&	13&	15&	9\\
-Transportation and Warehousing&	8&	8&	14&	33\\
-Prof., Scient., and Technical Serv.&	5&	10&	12&	1\\
-Manufacturing&	7&	5&	9&	10\\
-Agri., forestry, fishing \& hunting &	4&	1&	4&	23\\
+Wholesale Trade						&8	&12	&15	&12\\
+Transportation and Warehousing 		&8	&8	&14	&33\\
+Prof., Scient., and Technical Serv.	&5	&10	&12	&1\\
+Manufacturing 						&7	&5	&9	&10\\
+Agri., forestry, fishing \& hunting &4	&1	&4	&23\\
 
@@
 
-We see four avenues for further research.
-The first concerns the demand side of the economy, which we have mostly neglected by focusing on the production function.
-The employment response to a production disruption greatly depends on the elasticity of demand.
-We hypothesize that sectors like schooling and health care have inelastic demand and will continue to employ many workers despite significant disruptions.
-However, personal services, small grocery stores and restaurants may face more elastic demand and respond to large production cost increases by laying off a significant fraction of their work force.
-
-The second direction concerns the interaction between sectors and regions.
+We see three avenues for further research.
+The first concerns the interaction between sectors and regions.
 Whenever productivity in any business drops, this shock can propagate to its buyers and suppliers.
@@
 
-The third and forth directions concern the long-run response of businesses as they try to become more resilient to such shocks in the future.
+The second and third directions concern the long-run response of businesses as they try to become more resilient to such shocks in the future.
 Whether the share of telecommunication remains large in the long run depends crucially on how easily it substitutes for face-to-face interaction.
-In our model, the two are perfect substitutes with the only distinction that the efficiency of face-to-face meetings improves with population density, whereas telecommunication does not depend on agglomeration \cite{Rossi-Hansberg2007-tm,Ioannides2008-bs,Tian2019-wq}.
 Previous work has found face-to-face communication to be more effective in high-intensity communication which is particularly helpful to overcome incentive problems in joint production \cite{Gaspar1998-gy,Storper2004-mg}.
@@
 None of these papers discuss disruptions from social distancing measures.
-Further study of the modes of communication in the O*NET occupation survey can shed light on whether telecommunication can act as a low-cost substitute for face-to-face meetings.
 
-Fourth, businesses may change their location in response to perceived threats and disruptions.
-As we discussed, epidemics have a disproportionate effect on cities.
+Third, businesses may change their location in response to perceived threats and disruptions.
+Epidemics have a disproportionate effect on cities.
 So it is conceivable that in a post-pandemic spatial equilibrium (not modeled here, but see \cite{Tian2019-wq}), the agglomeration premium falls and firms find it less attractive to locate in cities.
@@
 \section*{Data Availability Statement}
-The mobility data used in this paper \cite{SafeGraph2020-gn} is confidential, but may be obtained free of charge for Covid-19-related research from the COVID-19 Consortium.
+The mobility data used in this paper \cite{SafeGraph2020-gn} is confidential, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium.
 Researchers interested in access to the data can apply at https://www.safegraph.com/covid-19-data-consortium.
@@
 \section*{Acknowledgments}
-We thank Gábor Békés, Péter Harasztosi, Péter Karádi, Balázs Lengyel, Dávid Krisztián Nagy, Andrea Weber, Charles Wyplosz, and an anonymous referee for comments.
+We thank Gábor Békés, Péter Harasztosi, Péter Karádi, Balázs Lengyel, Dávid Krisztián Nagy, Andrea Weber, Charles Wyplosz, and two anonymous referees for comments.
 

### 2020-07-22 text/content.tex
Minor changes
Point to v2.0

@@
 The mobility data used in this paper \cite{SafeGraph2020-gn} is confidential, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium.
-Researchers interested in access to the data can apply at https://www.safegraph.com/covid-19-data-consortium.
+Researchers interested in access to the data can apply at \url{https://www.safegraph.com/covid-19-data-consortium}.
 After signing a Data Agreement, access is granted within a few days.
@@
 ``Affected share'' refers to the share of workers in any of the three occupation groups.
-Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v1.3/data/derived/industry-index.csv}.
+Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v2.0/data/derived/industry-index.csv}.
 
@@
 ``Affected share'' refers to the share of workers in any of the three occupation groups.
-Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v1.3/data/derived/location-index.csv}.
+Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v2.0/data/derived/location-index.csv}.
 
@@
 \label{S3_URL}
-{\bf Replication code and data.} Replication code and data are available at \url{https://github.com/ceumicrodata/social-distancing/tree/v1.3}.
+{\bf Replication code and data.} Replication code and data are available at \url{https://github.com/ceumicrodata/social-distancing/tree/v2.0}.
 

### 2020-07-22 text/content.tex
Correct typos and table notes.
Resolves #16

@@
 This dataset measures the number of visits to a business in a given month, as captured from several cell phone apps and made available to researchers in an anonymized form.
-We study how the reduced number of customer vists is correlated with changes in sectoral employment.
+We study how the reduced number of customer visits is correlated with changes in sectoral employment.
 
@@
 Table \ref{table2} displays the top five and the bottom five industries by 2-digit NAICS industries as sorted by the percentage of workers in communication-intensive occupations, excluding hospitals and clinics.
-Across industries, retail trade, accommodation and food services, arts, entertainment, and recreation, other services and administrative and support and waste management and remediation services have the highest share of communication-intensive workers, exceeding 35 percent.
+Across industries, retail trade and accommodation and food services, arts, entertainment, and recreation have the highest share of communication-intensive workers, exceeding 35 percent.
 Information, transportation, production, professional, scientific, and technical Services and agricultural industries are less reliant on face-to-face communication.
@@
 
-As we see from the regression results above, the largest decline in sectoral employment are in sectors where the share of customer-facing workers is highest.
+As we see from the regression results above, the largest decline in sectoral employment is in sectors where the share of customer-facing workers is highest.
 We hence use the share of customer-facing workers for the following analysis.
@@
 \end{tabular}
-\begin{flushleft} ``Wage subsidy'' displays the percentage decrease in labor costs necessary to compensate businesses when worker contacts are reduced by half.
+\begin{flushleft} ``Wage subsidy'' displays the percentage decrease in labor costs necessary to compensate businesses for the reduced number of customer-worker contacts.
 ``Employment'' is the February 2020 employment of the sector in thousands \cite{CES}.

### 2020-07-22 text/content.tex
Update DAS with precise URI of data files and some more explanations of access
Re #15

@@
 \section*{Data Availability Statement}
-The mobility data used in this paper \cite{SafeGraph2020-gn} is confidential, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium.
+The mobility data used in this paper \cite{SafeGraph2020-gn} is proprietary, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium.
+The authors are not affiliated with this consortium.
 Researchers interested in access to the data can apply at \url{https://www.safegraph.com/covid-19-data-consortium}.
 After signing a Data Agreement, access is granted within a few days.
+The Consortium does not require coauthorship and does not preview or approve research reports before publication.
+Datafiles used: \texttt{/monthly-patterns/patterns\_backfill/2020/05/07/12/2020/02/ patterns-part[1-4].csv.gz} (data for February 2020, released May 7, 2020) and \texttt{/monthly-patterns/patterns/2020/06/05/06/patterns-part[1-4].csv.gz} (data for February 2020, released June 5, 2020).
 The authors will assist with any reasonable replication attempts for two years following publication.

### 2020-07-28 text/content.tex
Add more details to DAS
Resolves #15

@@
 The authors are not affiliated with this consortium.
-Researchers interested in access to the data can apply at \url{https://www.safegraph.com/covid-19-data-consortium}.
+Researchers interested in access to the data can apply at \url{https://www.safegraph.com/covid-19-data-consortium} (data manager: Ross Epstein, ross@safegraph.com).
 After signing a Data Agreement, access is granted within a few days.
-The Consortium does not require coauthorship and does not preview or approve research reports before publication.
+The Consortium does not require coauthorship and does not review or approve research results before publication.
 Datafiles used: \texttt{/monthly-patterns/patterns\_backfill/2020/05/07/12/2020/02/ patterns-part[1-4].csv.gz} (data for February 2020, released May 7, 2020) and \texttt{/monthly-patterns/patterns/2020/06/05/06/patterns-part[1-4].csv.gz} (data for February 2020, released June 5, 2020).
+The COVID-19 Consortium will keep these datafiles accessible for researchers.
 The authors will assist with any reasonable replication attempts for two years following publication.

### 2020-07-31 text/content.tex
Add Core Places to DAS

@@
 \section*{Data Availability Statement}
-The mobility data used in this paper \cite{SafeGraph2020-gn} is proprietary, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium.
+The mobility data used in thirds paper \cite{SafeGraph2020-gn} is proprietary, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium.
 The authors are not affiliated with this consortium.
@@
 The Consortium does not require coauthorship and does not review or approve research results before publication.
-Datafiles used: \texttt{/monthly-patterns/patterns\_backfill/2020/05/07/12/2020/02/ patterns-part[1-4].csv.gz} (data for February 2020, released May 7, 2020) and \texttt{/monthly-patterns/patterns/2020/06/05/06/patterns-part[1-4].csv.gz} (data for February 2020, released June 5, 2020).
+Datafiles used: \texttt{/monthly-patterns /patterns\_backfill/2020/05/07/12/2020/02/ patterns-part[1-4].csv.gz} (Monthly Places Patterns for February 2020, released May 7, 2020), \texttt{/monthly-patterns/patterns/2020/06/05/06/patterns-part[1-4].csv.gz} (Monthly Places Patterns for February 2020, released June 5, 2020) and \texttt{/core/2020 /06/Core-USA-June2020-Release-CORE\_POI-2020\_05-2020-06-06.zip} (Core Places for June 2020, released June 6, 2020).
 The COVID-19 Consortium will keep these datafiles accessible for researchers.

### 2020-07-31 text/manuscript.tex
Merge manuscript into one tex file

--- 2020-03-18 text/manuscript.tex
@@
 % color can be used to apply background shading to table cells only
-\usepackage[table]{xcolor}
+\usepackage{hyperref}
+\usepackage{tikz}
+%\usepackage[table]{xcolor}
 
@@
 \usepackage{array}
+\usepackage{dcolumn}
 
@@
 \noalign{\global\arrayrulewidth\savedwidth}}
+
+\providecommand\plos[1]{}
 
@@
 {\Large
-\textbf\newline{Which sectors are most prone to social distancing measures?} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Business disruptions from social distancing} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 % Primary Equal Contribution Note
-\Yinyang This author is responsible for the research idea, the theoretical model, the analysis of the spatial data and the first draft of the manuscript.
+\Yinyang This author is responsible for the research idea, the theoretical model, and the analysis of the customer mobility data.
+Both authors contributed equally to reviewing the analysis results and writing the manuscript.
 
@@
 % Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-\ddag This author is responsible for the analysis of the occupation data, reviewing and discussing results and editing the manuscript.
+\ddag This author is responsible for the analysis of the occupation data. Both authors contributed equally to reviewing the analysis results and writing the manuscript.
 
@@
 \section*{Abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
-Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-\section*{Author summary}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
-Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+Social distancing interventions can be effective against epidemics but are potentially detrimental for the economy.
+Businesses that rely heavily on face-to-face communication or close physical proximity when producing a product or providing a service are particularly vulnerable. 
+There is, however, no systematic evidence about the role of human interactions across different lines of business and about which will be the most limited by social distancing.
+Here we provide theory-based measures of the reliance of U.S. businesses on human interaction, detailed by industry and geographic location.
+We find that, before the pandemic hit, 35 million workers worked in occupations that rely heavily on face-to-face communication or require close physical proximity to other workers.
+Many of these workers lost their jobs since.
+Consistently with our model, employment losses have been largest in sectors that rely heavily on customer contact and where these contacts dropped the most: retail, hotels and restaurants, arts and entertainment and schools.
+Our results can help quantify the economic costs of social distancing.
 
@@
 
-% Use "Eq" instead of "Equation" for equation citations.
 \section*{Introduction}
-Social distancing measures are effective non-pharmaceutical interventions against the rapid spread of epidemics (REFs).
-Many countries have implemented or are considering measures such as school closures, prohibition of large gatherings and transportation to slow down the spread of the coronavirus (REFs).
+
+Social distancing measures are effective non-pharmaceutical interventions against the rapid spread of epidemics \cite{Bootsma2007-ww,Markel2007-ad,Hatchett2007-gc,Wilder-Smith2020-jj}.
+Many countries have implemented measures such as school closures, prohibition of large gatherings and restrictions on non-essential stores and transportation to slow down the spread of the 2019--20 coronavirus pandemic \cite{Anderson2020-qk,Cohen2020-jw,Thompson2020-lc,noauthor_2020-xi}.
 What are the economic effects of such social distancing interventions?
-Which are the firms and industries most affected by the restrictions?
+Which businesses are most affected by the restrictions?
 
-Past research has analyzed the efficacy of social distancing interventions on reducing the spread of epidemics using the 1918 Spanish Flu in the US (REF) and seasonal viral infections in France (REF) [add more REFs].
-Our knowledge of economic impacts, however, is limited.
-For this question, the case of the Spanish Flu pandemic is less relevant, as the importance of face-to-face communication has increased in the last 100 years through urbanization (REF) and XXX services (REF).
+Past research has analyzed the efficacy of social distancing interventions on reducing the spread of epidemics using the 1918 Spanish Flu in the U.S.
+\cite{Hatchett2007-gc,Markel2007-ad,Bootsma2007-ww} and seasonal viral infections in France \cite{Adda2016-mn}.
+Our knowledge of economic impacts, however, is limited \cite{Wren-Lewis2020-vc}.
+For this question, past data may be less relevant, as the importance of face-to-face communication has increased steadily in the last 100 years through urbanization \cite{Henderson2010-mv,Henderson2002-ji} and specialization increased in business services as well \cite{Herrendorf2014-jx,Duarte2019-kc}.
+Even if advances in information and communication technology made it increasingly possible to communicate with co-workers and customers without the need for physical face-to-face interactions, personal contacts are still inevitable in some industries \cite{Dingel2020-lh,von2020labour}.
 
-\section{A model of }
+The starting point of this paper is the observation that many sectors rely heavily on face-to-face communication in the production process \cite{Charlot2004-zr,Tian2019-wq}.
+We build a model of communication to understand how limiting face-to-face interaction increases production costs.
+Without social distancing, workers specialize in a narrow range of tasks and interact with other workers completing other tasks.
+This division of labor reduces production costs but requires frequent contact between workers.
+In the model, the number of contacts per worker is the most frequent in businesses where the division of labor is important.
+When face-to-face interaction is limited, these are exactly the businesses that suffer the most.
 
-\section{Methodology}
-We compute two measures of exposure to social distancing interventions.
-The first is the share of workers whose job requires personal communications.
-This is high for sectors like XX and low for sectors like XX.
-The idea is that when workers in communication-intensive occupations stay at home, their productivity decreases.
-A challenge to this assumption is that, in some occupations, online communication can partly substitute face-to-face communication.
+To measure business disruptions from social distancing, we turn to recent data on the task descriptions of each occupation \cite{National_Center_for_ONET_Development2020-wj}, the precise geographic location of non-farm businesses in the U.S.
+\cite{CBP}, and customer mobility patterns \cite{SafeGraph2020-gn}.
+We construct three groups of occupations.
+First, some occupations require face-to-face communication several times a week with other workers.
+Examples of these \emph{teamwork-intensive} occupations include maintenance, personal care related occupations and health care professionals.
+Other occupations require frequent face-to-face contact with customers.
+Retail salespersons, social workers and waiters and waitresses are examples of such \emph{customer-facing} occupations.
+The third group of workers may need to be in physical proximity of one another even if they do not communicate, for example, to operate machinery or access key resources.
+Examples of such occupations requiring \emph{physical presence} are drivers and machine operators, especially in mining and water transport, where crammed working environments are common.
+With our occupation level measures, we aim to capture the jobs that can be performed less efficiently from home.
+We validate our indexes by using the American Time Use Survey (ATUS) \cite{ATUS}, which directly asks about the possibility of working from home.
 
-The second measure captures how urbanized workers are: what fraction of them work in high population or employment density areas.
-This is high for sectors like XX and low for sectors like XX.
-When the demand for face-to-face communication, either within the firm or with consumers is large, firms are likely to agglomerate in large cities.
-The challenge to this measure is that agglomeration may also be driven by a minimization of transportation costs.
+To study how the patterns of interaction have changed in the U.S.
+during the Covid-19 pandemic, we use customer mobility data from SafeGraph \cite{SafeGraph2020-gn}.
+This dataset measures the number of visits to a business in a given month, as captured from several cell phone apps and made available to researchers in an anonymized form.
+We study how the reduced number of customer visits is correlated with changes in sectoral employment.
 
-Taken together, high values of both measures of communication intensity and agglomeration coefficient can indicate that face-to-face communication (as opposed to online communication or transportation) is used intensively in the sector.
+\section*{A model of communication}
+When workers communicate with others, they can divide labor more effectively.
+Production involves sequentially completing tasks indexed by $z\in[0,1]$.
+A single worker can do a range of tasks, but there is a benefit to specialization and division of labor \cite{Smith1778-qq,Becker1992-ac}.
+The labor cost of a worker completing $Z<1$ measure of tasks is $Z^{1+\gamma}/\gamma$, where $\gamma>0$ captures the benefits to the division of labor.
+As we show below, the higher the $\gamma$, the more specialized each worker will be in a narrower set of tasks.
+Without loss of generality, we normalize the wage rate of workers to one so that all costs are expressed relative to worker wages.
 
-\section{Data}
-ONET
-CBP density
-CBP plant size
+Once the range of tasks $Z$ is completed, the worker passes the unfinished product on to another worker.
+This has a cost of $\tau$, which can capture the cost of communicating and interacting across workers.
+The determinants of communication cost will be parametrized later.
+After all the tasks are completed, another step of communication with cost $\tau$ is needed to deliver the product to the customer.
+This cost leads to the Marshallian externality that firms want to be close to their customers and customers want to be close to their suppliers \cite{Marshall1920-ps,Krugman1991-gr}.
 
-## Cross walks
-## Construction of communication index
-## Worker density
+The firm will optimally decide how to share tasks between workers.
+The key trade-off is economizing on the cost of communication while exploiting the division of labor \cite{Becker1992-ac}.
+Let $n$ denote the number of workers involved in the production process.
+Because workers are symmetric, each works on $Z=1/n$ range of tasks before passing the work to the next worker.
+Production involves $n-1$ ``contacts'' (instances of communication) and there is an additional contact with the customer.
 
-Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+Fig \ref{fig1} illustrates the division of labor between workers.
+Horizontal movement represents production along a range of tasks ($Z=1/n$), vertical movement represents interaction ($\tau$).
+We note three potential interpretations of our model.
+First, when workers work in teams, they can efficiently divide labor among themselves (panel A).
+The benefit of a larger team is better specialization.
+Law firms, management teams, and IT service firms are prime examples of businesses where intensive communication leads to narrow specialization \cite{Garicano2009-jv}.
+Second, communication may involve the customer (panel B).
+The benefit of more frequent interaction with the customer is a product or service that is better suited to their needs.
+Restaurants, beauty salons, personal and social services require such frequent interaction exactly because their service is so customized.
+Third, workers may need access to a key physical resource (panel C).
+In this case, even if they do not communicate, they may be subject to social distancing measures.
+For example, operators of machines, vehicle drivers or workers on an oil rig are all very much tied to a key resource to do their job.
+The key assumption behind all three interpretations is that frequent interaction increases productivity, whether happening between workers, between workers and customers, or between workers and machines.
 
-\begin{eqnarray}
-\label{eq:schemeP}
-	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
-\end{eqnarray}
+\begin{figure}[!h]
+\plos{\input{fig1a-input}\input{fig1b-input}\input{fig1c-input}}
 
-\section*{Materials and methods}
-\subsection*{Etiam eget sapien nibh}
-
-% For figure citations, please use "Fig" instead of "Figure".
-Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
-
-% Place figure captions after the first paragraph in which they are cited.
-\begin{figure}[!h]
-\caption{{\bf Bold the figure title.}
-Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
+\caption{{\bf Patterns of interaction in the workplace.}
+Horizontal movement represents production, vertical movement represents interaction.
+(A) Each worker W works on a range $1/n$ of tasks, passing work $n-1$ times.
+(B) Worker W and customer C engage in frequent interactions.
+(C) Each worker W needs physical access to a key resource R.}
 \label{fig1}
@@
 
-% Results and Discussion can be combined.
-\section*{Results}
-Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
+The firm's cost minimization problem can then be written as a function of the number of contacts alone,
+\begin{equation}\label{TC}
+	c(\tau) = \min_n n\tau + \frac 1\gamma n^{-\gamma},
+\end{equation}
+where total communication costs are $n\tau$ and production costs are $n Z^{1+\gamma}/\gamma$ with $Z=1/n$.
 
-% Place tables after the first paragraph in which they are cited.
+Given the strict convexity of this cost function, and ignoring integer problems, the first-order condition is necessary and sufficient for the optimum,
+\begin{equation}\label{nstar}
+	n^*(\tau) = \tau^{-1/(1+\gamma)}.
+\end{equation}
+The number of worker contacts is decreasing in the cost of communication, expressed relative to worker wage.
+When the division of labor is important, $\gamma$ is high, and the number of contacts does not depend very strongly on communication costs.
+
+The total cost of producing one good can be calculated by substituting in \eqref{nstar} into \eqref{TC},
+\begin{equation}\label{cost}
+	c(\tau) = \tau^{\chi}/\chi,
+\end{equation}
+where $\chi=\gamma/(1+\gamma)\in(0,1)$ measures the importance of division of labor.
+This unit cost function is the same as if workers and communication were substitutable in the production function in a Cobb-Douglas fashion.
+Indeed, $\chi$ captures the share of costs associated with communication and can be calibrated accordingly.
+
+\subsection*{Social distancing}
+
+We study the effect of social distancing, which reduces the number of face-to-face contacts to some exogenous value $N$.
+This may be mandated by government orders to close certain places of business or stay at home.
+But it can also be the result of voluntary social distancing in response to the risk of infection.
+
+The optimal number of contacts without social distancing is given by Eq \eqref{nstar}.
+Firms with $n^*>N$ are limited by social distancing.
+Their unit cost will increase to $c' = N \tau + N^{-\gamma}/\gamma$, which is greater than the optimal cost,
+\begin{equation}\label{socdist}
+\frac{c'}{c} 
+	= \chi \frac{N}{n^*} + (1-\chi) \left(\frac{N}{n^*}\right)^{-\gamma}>1.
+\end{equation}
+The first term of the weighted average is less than one, representing a reduction in communication costs once the number of contacts declines.
+The second term is greater than one due to the fact that every worker has to complete a wider range of tasks than before, and they lose the benefit of specialization.
+Because $n^*$ is the cost-minimizing communication choice of the firm, the second term dominates, and production costs increase with social distancing.
+
+\section*{Data and methodology}
+To estimate the potential disruptions from social distancing, we need a measure of the importance of worker interaction (corresponding to $\chi$ in the model) and its change (captured by the ratio $N/n^*$).
+
+Let $\xi_o$ denote an indicator equal to one if occupation $o$ is interaction-intensive and zero otherwise.
+For industry $i$, $\chi_i = \sum_o s_{io}\xi_o$ measures the fraction of workers in affected occupations, with $s_{io}$ denoting the employment share of occupation $o$ in industry $i$.
+
+We use the Occupational Information Network (O*NET) \cite{National_Center_for_ONET_Development2020-wj} to measure the characteristics of a given occupation, similarly to previous studies \cite{Firpo2011-hp,Autor2013-sh,Jin2020-tq,Dingel2020-lh,Leibovici2020-qr,Mongey2020-qc}.
+The O*NET dataset contains detailed standardized descriptions on almost 1,000 occupations along eight dimensions.
+We focus on job characteristics that are related to recent social distancing measures, while prior work focused mainly on measuring offshorability of the given tasks \cite{Firpo2011-hp,Autor2013-sh}.
+
+Social distancing interventions limit the interaction between people and regulate physical proximity between individuals.
+We thus focus on three related job characteristics based on work context and work activity described in O*NET.
+The first two indicators capture how communication-intensive the job is.
+Communication can be of two types: internal communication with co-workers (\emph{teamwork}) or external communication directly with customers (\emph{customer-facing}).
+The third indicator takes into consideration the possibility that workers may need to be in physical proximity of one another even if they do not communicate.
+We create an index that shows how important \emph{physical presence} is to perform a given job.
+Table \ref{table1} details the specific O*NET indexes that contribute to each of our three measures.
+As social distancing measures only limit personal communication, for communication indexes, we require that the necessary face-to-face communication happens at least several times a week.
+Face-to-face meetings can often be substituted by more structured communication, for which working from home is not as disruptive.
+To allow for this possibility, we only classify occupations as teamwork-intensive or customer-facing where both emails and letters and memos are less frequent forms of communication than face-to-face meetings.
+This excludes most managers and certain business services.
+Similarly, for physical presence, we require at least a certain degree of proximity to other workers which corresponds to working in a shared office.
+
 \begin{table}[!ht]
 \begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
 \caption{
-{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-\begin{tabular}{|l+l|l|l|l|l|l|l|}
+{\bf Definition of social distancing indexes.}}
+\begin{tabular}{|l+l|l|}
 \hline
-\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
-$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
-$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
-$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
+{\bf Index} & {\bf Tasks} & {\bf Context} 
+\\ \thickhline
+\hline
+Teamwork & Work With Work Group or Team & Face-to-face  \\
+& Provide Consultation and Advice to Others & discussions  \\
+& Coordinating the Work and Activities of Others & several times a week \\
+& Guiding Directing and Motivating Subordinates & \& more often than \\
+& Developing and Building Teams & emails, letters, memos\\
+\hline
+Customer & Deal With External Customers & Face-to-face\\
+&  Performing for or Working Directly with the Public & discussions \\
+& Assisting and Caring for Others & several times a week \\
+& Provide Consultation and Advice to Others & \& more often than\\
+& Establishing and Maintaining Interpersonal Relationships & emails, letters, memos \\
+\hline
+Presence & Handling and Moving Objects & Density of \\
+& Operating Vehicles, Mechanized Devices or Equipment & co-workers \\
+& Repairing and Maintaining Electronic Equipment &  like shared\\
+& Repairing and Maintaining Mechanical Equipment & office or more\\
+& Inspecting Equipment, Structures, or Material &\\
+\hline
+\hline
 \end{tabular}
-\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
+\begin{flushleft} Each social distancing index (column 1) is created as an arithmetic average of the component indexes (column 2).
+To be classified an affected occupation, the average has to exceed 62.5 and the work context index has to exceed the threshold in column 3.
 \end{flushleft}
@@
 
-%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
-\subsection*{\lorem\ and \ipsum\ nunc blandit a tortor}
-\subsubsection*{3rd level heading} 
-Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
-Sed non aliquet felis.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet.
-Sed suscipit iaculis mi at feugiat.
+We aggregate the measures to 6-digit occupation codes (Standard Occupational Classification; 2010-SOC).
+We have information on the relevance of teamwork, customer contact and physical presence  for 809 occupations in SOC 2010 codes.
 
-\begin{enumerate}
-	\item{react}
-	\item{diffuse free particles}
-	\item{increment time by dt and go to 1}
-\end{enumerate}
+Teamwork and customer contacts are highly correlated (Fig \ref{fig3}), but they are conceptually different.
+While all medical occupations require teamwork and customer contact, supervisors in general are working in teams but do not often communicate directly with customers.
+Machine operators and production workers in general are at the bottom of both of the distributions.
+As managers can substitute personal communication with emails, they are not considered in general as teamwork-intensive occupations according to our definition.
+Given the high correlation between the two types of communication, we often refer to \emph{communication-intensive} occupations that are either teamwork-intensive or customer-facing.
 
-\subsection*{Sed ac quam id nisi malesuada congue}
+\begin{figure}[!h]
+\plos{\includegraphics[width=0.7\linewidth]{fig3.pdf}}
 
-Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
+\caption{{\bf Teamwork and customer contact are highly correlated.}
+Each circle represents an occupation. Teamwork and customer contact indexes are constructed as explained in main text.}
+\label{fig3}
+\end{figure}
 
-\begin{itemize}
-	\item First bulleted item.
-	\item Second bulleted item.
-	\item Third bulleted item.
-\end{itemize}
+With our occupation-level measures, we aim to capture the type of activities that require frequent face-to-face contact.
+Our assumption is that these activities cannot be effectively done from home.
+To validate this assumption, we use data from the American Time Use Survey (ATUS) \cite{ATUS}, which directly asks workers whether they \emph{can} work from home.
+Fig \ref{customer_validation} plots our customer-intensity measure, for each occupation, against the share of workers who reported in ATUS that they can work from home (dark filled circles).
+Indeed, most customer-facing occupations have very few workers who can work from home.
+The pattern is different if we look at occupations that rely more on email, letters, and memos for customer communication (light hollow circles).
+The majority of these workers can work from home.
+Interestingly, for each degree of working from home (horizontal axis), there is sufficient variation in the importance of customer contact (vertical axis).
+The same patterns can be observed for teamwork-intensive occupations (Fig \ref{teamwork_validation}).
+This makes use conclude that dropping occupations primarily relying on email, letters and memos is sufficient to control for the potential to work from home.
 
-\section*{Discussion}
-Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero~\cite{bib3}.
+\begin{figure}[!h]
+\plos{\includegraphics[width=0.7\linewidth]{customer_atus_validation.pdf}}
 
-\section*{Conclusion}
+\caption{{\bf Workers in customer-facing occupations with face-to-face interaction can rarely work from home.}
+Filled circles represent the occupations where face-to-face contacts are more important than emails and memos.
+Hollow circles represent the occupations where emails and memos are more important than face-to-face contacts.
+The indexes are constructed as explained in main text.
+}
+\label{customer_validation}
+\end{figure}
 
-CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
+\begin{figure}[!h]
+\plos{\includegraphics[width=0.7\linewidth]{teamwork_atus_validation.pdf}}
 
-Sed non aliquet felis.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet.
-Sed suscipit iaculis mi at feugiat.
-Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna.
-Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-Nam condimentum sem eget mollis euismod.
-Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex.
-Nunc est dui, sodales sed mauris nec, auctor sagittis leo.
-Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor.
-For more information, see \nameref{S1_Appendix}.
+\caption{{\bf Workers in teamwork-intensive occupations with face-to-face interaction can rarely work from home.}
+Filled circles represent the occupations where face-to-face contacts are more important than emails and memos.
+Hollow circles represent the occupations where emails and memos are more important than face-to-face contacts.
+The indexes are constructed as explained in main text.
+}
+\label{teamwork_validation}
+\end{figure}
+
+With our validated occupation measures in hand, our next step is to calculate for each sector the share of workers whose job requires a high level of teamwork, customer contact, and physical presence.
+We use the same sectoral breakdown as the Current Employment Statistics (CES) \cite{CES}.
+As all the indexes are an absolute value running from 0 to 100, we use 62.5 as a cutoff to define a job to be teamwork-intensive, customers contact-intensive, or job that requires physical presence from the worker.
+The occupation structure of the industries are retrieved from the official industry-occupation matrix \cite{employment-matrix}, we use the employment statistics by occupation-industry for February 2020.
+
+Based on the share of relevant occupations in industry employment, the most teamwork-intensive sectors are, for example ``Hospitals,'' ``Accommodation'' and  ``Motion picture and sound recording industries.'' In contrast, teamwork is not important in sectors like ``Forestry and logging'' and ``Fishing, hunting and trapping.''  Customer contact is relevant in sectors like ``Hospitals''  and ``Retail'', while it is not relevant is sectors line ``Truck transportation,'' and ``Forestry and logging.'' Physical presence is relevant in sectors like  ``Truck transportation,'' ``Repair and maintenance,'' mining in general, while it is not relevant in finance and information technology sectors.
+
+``Hospitals'' score high on all three measures because communication in health care teams and with patients is important, and doctors and nurses work in close physical proximity to others.
+We nonetheless remove this sector from the analysis because of its inevitable direct role in combating the epidemic which is not captured well in a simple model of communication.
+
+To measure how the number of interactions has changed due to social distancing, we use data from SafeGraph \cite{SafeGraph2020-gn}, a data company that aggregates anonymized location data from numerous applications to provide insights about physical places.
+To enhance privacy, SafeGraph excludes census block group information if fewer than five devices visited an establishment in a month from a given census block group.
+
+We use the Monthly Patterns file that captures the number of visits by mobile devices in the sample to more than 4 million points of interest (POIs) in each month.
+Each POI is assigned a specific address, including a ZIP code, and a 6-digit NAICS code.
+Because the pandemic hit different regions of the U.S.
+at different times, we use both the industry and the regional variation of customer mobility data.
+We aggregate monthly visits by 3-digit NAICS code and ZIP code.
+This enables us to measure by how much, for example, visits to clothing stores have declined in downtown Manhattan.
+
+We measure the percentage change in the number of visits between February and May 2020.
+When the industry-ZIP cell received fewer than ten visits in either month or when visits data are missing in SafeGraph, we replace the change in visits with the average of the ZIP code.
+
+To validate the customer mobility data, we check the location of sectors in the County Business Patterns (CBP) data for 2017 \cite{CBP}.
+For a finer spatial resolution, we use the data tabulated by ZIP-Code Tabulation Areas.
+The CBP lists the number of establishments of a certain size for each ZIP-code and NAICS industry code.
+We estimate the employment of each industry in each ZIP code to be able to compute employment-weighted national averages of our statistics of interest.
+
+Because establishment sizes are given in bins (e.g., 1--4 employees), we take the midpoint of each bin as our estimated employment (e.g., 2.5 employees).
+In small industries and ZIP codes, the Census omits some size categories to protect the confidentiality of businesses.
+We impute employment in these plants from the national size distribution of plants in the same NAICS industry.
+Our estimated industry-level employment is a very good approximation to official employment statistics \cite{CES}.
+The correlation between our estimates based on CBP and the employment reported in CES is 0.98.
+
+\subsection*{Counterfactual calculations}
+To gauge the magnitude of the effect of social distancing, we compute the effect of the decline in the number of customer-worker contacts.
+At the same time, we let the government introduce a proportional wage subsidy $\lambda$ to help offset the costs from lower interaction.
+With this subsidy, the cost of labor will be $(1-\lambda)$.
+
+We ask what level of $\lambda$ would exactly compensate businesses for the communication disruption caused by social distancing.
+When interactions decrease, $N<n^*$, production costs increase.
+We compute the subsidy $\lambda$, which, when given to every worker, would exactly offset the cost increase.
+This way the business would not have to fire any of its workers.
+The goal of this exercise is not to evaluate any particular employment support policy, but to get a sense of the magnitude of business disruptions.
+
+Using the cost change in Eq \ref{socdist}, we can express the compensating labor subsidy of industry $i$ in region $r$ as
+\begin{equation}\label{subsidy}
+    \lambda_{ir} = 1 -
+        \frac{1-\chi_i}{1-\chi_i N_{ir}/n_{ir}^*}
+        \left(
+        \frac{N_{ir}}{n_{ir}^*}
+        \right)^{\gamma_i}>0.
+\end{equation}
+We calibrate $n_{ir}^*$ to match the number of customer visits to establishments of industry $i$ in ZIP-code $r$ in February 2020, assuming that these visits were optimal before the pandemic hit the U.S.
+The new number of visits, $N_{it}$ will be calibrated to the number of customer visits in May 2020.
+The compensating wage subsidy increases in the importance of communication $\chi_i$ and decreases in the change in contacts $N_{ir}/n^*_{ir}$.
+The subscripts note that communication share is industry specific and the change in contacts is both industry and region specific.
+
+To calibrate the importance of communication $\chi_i$, note that it is the cost share of communication, and can be correspondingly calibrated to the employment share of communication-intensive occupations in industry $i$.
+We then compute the compensating wage subsidy for each industry in each ZIP code using Eq \ref{subsidy}.
+We report employment-weighted averages of this across sectors and across locations.
+
+\section*{Results}
+Table \ref{table2} displays the top five and the bottom five industries by 2-digit NAICS industries as sorted by the percentage of workers in communication-intensive occupations, excluding hospitals and clinics.
+Across industries, retail trade and accommodation and food services, arts, entertainment, and recreation have the highest share of communication-intensive workers, exceeding 35 percent.
+Information, transportation, production, professional, scientific, and technical Services and agricultural industries are less reliant on face-to-face communication.
+This heterogeneity across industries is important to understand the effect of social distancing measures.
+
+\begin{table}[!ht]
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\caption{
+{\bf Retail, accommodation and restaurants are the most communication intensive.}}
+\begin{tabular}{|l+c|c|c+c|}
+\hline
+ & \multicolumn{3}{c}{\bf Communication} &  
+\\ 
+{\bf Industry} & {\bf Teamw.} & {\bf Custom.} & {\bf Overall} & {\bf Presence} 
+\\ \thickhline
+Retail trade 						&13	&66	&67	&5\\
+Accommodation \& food services 		&8	&50	&51	&1\\
+Arts, Entertainment, and Recreation &12	&38	&40	&2\\
+Other Services (except Public Admin.)&12&30	&33	&12\\
+Admin. \& Support \& Waste Manag.  	&17	&24	&27	&7\\
+...&&&&\\
+Wholesale Trade						&8	&12	&15	&12\\
+Transportation and Warehousing 		&8	&8	&14	&33\\
+Prof., Scient., and Technical Serv.	&5	&10	&12	&1\\
+Manufacturing 						&7	&5	&9	&10\\
+Agri., forestry, fishing \& hunting &4	&1	&4	&23\\
+
+ \thickhline
+
+\hline
+\end{tabular}
+\begin{flushleft} ``Teamw.'' and ``Custom.'' show the percentage of workers in teamwork-intensive and customer-facing occupations, respectively.
+``Overall'' shows the percentage of workers in communication-intensive occupations that are either teamwork-intensive or customer-facing.
+It is less than the sum of the two indexes because some occupations rely on both types of communication.
+``Presence'' shows the percentage of workers whose jobs require physical presence in close proximity to others.
+\end{flushleft}
+\label{table2}
+%\end{adjustwidth}
+\end{table}
+
+Table \ref{table4} reports the results of regressing the log change in industry employment between February and May 2020 on our social distancing indexes.
+Each regression is estimated with unweighted ordinary least squares.
+Across the entire non-farm economy, employment has dropped by 13 percent (not seasonally adjusted) \cite{CES}.
+
+As Column 1 shows, the drop was larger in industries with a larger share of customer-facing workers.
+There is no significant correlation between the share of workers with teamwork-intensive jobs or the share of workers requiring physical presence to do their work and employment losses.
+In Column 2, we control for the change in log customer visits.
+Indeed, changes in customer visits are positively correlated with changes in employment (both dropping for most of our industries).
+In Column 3, we introduce interactions with the change in log customer visits (as a proxy for $\ln (N/n^*)$) and the share of communication workers (as a proxy for $\chi$).
+As predicted by the model, the drop in customer visits has the largest effect on sectoral employment in sectors where the share of customer-facing workers is highest.
+
+\begin{table}[!ht]
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\caption{
+{\bf Employment decline was sharpest in customer-facing industries.}}
+\input{regression.tex}
+\begin{flushleft} Regression results of change in log industry employment between February and May 2020 estimated by ordinary least squares (unweighted).
+Explanatory variables in Column 1 are the shares of customer-facing, teamwork-intensive and presence-requiring workers.
+Column 2 controls for the change in log monthly visits to industry establishments.
+Column 3 interacts the change in visits with the share of face-to-face intensive  workers in the two occupation groups.
+Robust standard errors are reported in parentheses.
+$p$-values are denoted by asterisk: * $<.1$ ** $<.05$ *** $<.01$.
+Sample excludes hospitals, clinics, and government establishments, as well as farming and fishing which are not present in CBP.
+\end{flushleft}
+\label{table4}
+%\end{adjustwidth}
+\end{table}
+
+As we see from the regression results above, the largest decline in sectoral employment is in sectors where the share of customer-facing workers is highest.
+We hence use the share of customer-facing workers for the following analysis.
+
+In the calibrated model, the social distancing that took place between February and May 2020 would be compensated by a 39.9 percent wage subsidy.
+The distribution of the compensating wage subsidy is, however, unequal across industries.
+Retail trade, where customer visits practically ground to a halt, would require a 234 percent wage subsidy.
+By contrast, the compensating wage subsidy in agriculture, transportation and manufacturing would be less than 2 percent (Table \ref{table3}).
+
+\begin{table}[!ht]
+%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\caption{
+{\bf The five most affected sectors require more than 14 percent wage subsidy.}}
+\begin{tabular}{|l+c|c|}
+\hline
+{\bf Industry} & {\bf Wage subsidy} & {\bf Employment} 
+\\ \thickhline
+Retail Trade	&234	&15,672\\
+Arts, Entertainment, and Recreation	&30.2	&2,472\\
+Accommodation and Food Services	&26.1	&14,394\\
+Educational Services	&22.2	&3,8328\\
+Other Services (except Public Admin.)	&14.5	&5,941\\
+...&&\\
+Mining          &2.0    &660\\
+Wholesale Trade	&1.8	&5,934\\
+Construction	&1.1	&7,639\\
+Manufacturing	&1.1	&12,852\\
+Agriculture, Forestry, Fishing and Hunting	&0.5	&55\\
+\hline
+{\bf Average} & {\bf 39.9} & {\bf 116,441}\\
+ \thickhline
+
+\hline
+\end{tabular}
+\begin{flushleft} ``Wage subsidy'' displays the percentage decrease in labor costs necessary to compensate businesses for the reduced number of customer-worker contacts.
+``Employment'' is the February 2020 employment of the sector in thousands \cite{CES}.
+The last row shows the employment-weighted average wage subsidy.
+Table excludes hospitals, clinics, and government establishments which are not present in CBP.
+\end{flushleft}
+\label{table3}
+%\end{adjustwidth}
+\end{table}
+
+\section*{Discussion and conclusions}
+
+The main cost of social distancing in our model is insufficient division of labor.
+This mechanism is motivated by \cite{Smith1778-qq} and captures the same trade-off as \cite{Becker1992-ac}.
+Our contribution is specifying the cost function in such a way that can be easily mapped to the data.
+
+More broadly, our argument is that frequent interaction increases productivity irrespective whether it is happening between workers, between workers and customers, or between workers and machines.
+In the main part of the empirical analysis, we focused only on the first two types of interactions, while we were silent about the third.
+But social distancing measures also affect sectors where workers need to be in physical proximity of one another even if they do not communicate, for example, to operate machinery or access key resources.
+This is relevant in sectors like ``Mining, Quarrying, and Oil and Gas Extraction'' and ``Transportation'' while it is not relevant in sectors like ``Finance and Insurance'' and ``Professional, Scientific, and Technical Services.''
+
+To a greater or lesser extent, all sectors will be affected by social distancing.
+Some sectors are hit by the intervention due to restricted face-to-face communication, others are hit due to restricting physical proximity of people.
+Some sectors are less affected across all dimensions.
+Examples include ``Fishing, hunting and trapping,'' ``Printing and related support activities,'' and manufacturing in general.
+
+Our results are consistent with parallel research on the overall economic effects of the coronavirus pandemic using O*NET data.
+Recent research found that about 34 percent of U.S.
+jobs can be performed from home \cite{Dingel2020-lh}.
+However, as our analysis points out, even among jobs that do not fall into this category, some are more at risk from social distancing than others.
+The share of workers working in close physical proximity to other people is similar to other recent estimates \cite{Leibovici2020-qr}.
+Workers in this group are found to be the most vulnerable across a wide range of socio-economic measures \cite{Jin2020-tq,Mongey2020-qc}.
+We contribute to this work by (i) building a model to understand how social distancing measures affect the production, (ii) identifying three groups of occupations affected by social distancing and (iii) validating our model with customer visit and employment data.
+
+We see three avenues for further research.
+The first concerns the interaction between sectors and regions.
+Whenever productivity in any business drops, this shock can propagate to its buyers and suppliers.
+The aggregate consequences of the epidemic will hence be modulated by input-output linkages between sectors, regions and countries \cite{Caliendo2014-mr,Caselli2020-nf,Baldwin2020-wb,Barrot2020-jf}.
+
+The second and third directions concern the long-run response of businesses as they try to become more resilient to such shocks in the future.
+Whether the share of telecommunication remains large in the long run depends crucially on how easily it substitutes for face-to-face interaction.
+Previous work has found face-to-face communication to be more effective in high-intensity communication which is particularly helpful to overcome incentive problems in joint production \cite{Gaspar1998-gy,Storper2004-mg}.
+Data on internet flows suggests that telecommunication is not a good substitute for face-to-face meetings \cite{Cuberes2013-js}.
+None of these papers discuss disruptions from social distancing measures.
+
+Third, businesses may change their location in response to perceived threats and disruptions.
+Epidemics have a disproportionate effect on cities.
+So it is conceivable that in a post-pandemic spatial equilibrium (not modeled here, but see \cite{Tian2019-wq}), the agglomeration premium falls and firms find it less attractive to locate in cities.
+A poignant point of comparison is the increased threat of terrorism in major cities following devastating attacks on New York, Washington, London, Paris, Madrid, Moscow and Mumbai.
+The general conclusion about terror threat is that cities have remained resilient and a robust attractor of businesses \cite{Glaeser2002-mw,Harrigan2002-ik}.
+We speculate that epidemics and social distancing can be more detrimental to cities than terror threats, because they tear apart the very fabric of urban life.
+However, we have limited data to make further predictions.
+
+\section*{Data Availability Statement}
+The mobility data used in thirds paper \cite{SafeGraph2020-gn} is proprietary, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium.
+The authors are not affiliated with this consortium.
+Researchers interested in access to the data can apply at \url{https://www.safegraph.com/covid-19-data-consortium} (data manager: Ross Epstein, ross@safegraph.com).
+After signing a Data Agreement, access is granted within a few days.
+The Consortium does not require coauthorship and does not review or approve research results before publication.
+Datafiles used: \texttt{/monthly-patterns /patterns\_backfill/2020/05/07/12/2020/02/ patterns-part[1-4].csv.gz} (Monthly Places Patterns for February 2020, released May 7, 2020), \texttt{/monthly-patterns/patterns/2020/06/05/06/patterns-part[1-4].csv.gz} (Monthly Places Patterns for February 2020, released June 5, 2020) and \texttt{/core/2020 /06/Core-USA-June2020-Release-CORE\_POI-2020\_05-2020-06-06.zip} (Core Places for June 2020, released June 6, 2020).
+The COVID-19 Consortium will keep these datafiles accessible for researchers.
+The authors will assist with any reasonable replication attempts for two years following publication.
+
+The code and all other data underlying our analysis are licensed for public use and will be made available on Zenodo.
 
@@
 % Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Fig.}
-\label{S1_Fig}
-{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
+\paragraph*{S1 Full table of sectors.}
+\label{S1_File}
+{\bf Social distancing exposure by sector.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the industry.
+``Communication share'' refers to the share of workers who are either teamwork-intensive or customer-facing.
+``Affected share'' refers to the share of workers in any of the three occupation groups.
+Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v2.0/data/derived/industry-index.csv}.
 
-\paragraph*{S2 Fig.}
-\label{S2_Fig}
-{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
+\paragraph*{S2 Full table of ZIP-codes.}
+\label{S2_File}
+{\bf Social distancing exposure by location.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the ZIP code.
+``Communication share'' refers to the share of workers who are either teamwork-intensive or customer-facing.
+``Affected share'' refers to the share of workers in any of the three occupation groups.
+Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v2.0/data/derived/location-index.csv}.
 
-\paragraph*{S1 File.}
-\label{S1_File}
-{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Video.}
-\label{S1_Video}
-{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Appendix.}
-\label{S1_Appendix}
-{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Table.}
-\label{S1_Table}
-{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
+\paragraph*{S3 Data repository.}
+\label{S3_URL}
+{\bf Replication code and data.} Replication code and data are available at \url{https://github.com/ceumicrodata/social-distancing/tree/v2.0}.
 
 \section*{Acknowledgments}
-Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-Nam id pretium nisi.
-Sed ac quam id nisi malesuada congue.
-Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
+We thank Gábor Békés, Péter Harasztosi, Péter Karádi, Balázs Lengyel, Dávid Krisztián Nagy, Andrea Weber, Charles Wyplosz, and two anonymous referees for comments.
 
@@
 
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% or
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here. See http://journals.plos.org/plosone/s/latex for 
-% step-by-step instructions.
-% 
-\begin{thebibliography}{10}
+%\begin{thebibliography}{10}
 
-\bibitem{bib1}
-Conant GC, Wolfe KH.
-\newblock {{T}urning a hobby into a job: how duplicated genes find new
-  functions}.
-\newblock Nat Rev Genet. 2008 Dec;9(12):938--950.
+%\end{thebibliography}
 
-\bibitem{bib2}
-Ohno S.
-\newblock Evolution by gene duplication.
-\newblock London: George Alien \& Unwin Ltd. Berlin, Heidelberg and New York:
-  Springer-Verlag.; 1970.
-
-\bibitem{bib3}
-Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
-\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
-  infection through a transposon insertion followed by a {D}uplication}.
-\newblock PLoS Genet. 2011 Oct;7(10):e1002337.
-
-\end{thebibliography}
+\bibliography{socdist}
 
 \end{document}
+
+%% Eichenbaum2020-gu
+%% Becker1992-ac
+
+%% put citation keys here for tab completion
+%% Storper2004-mg, Rosvall2005-jy, Moretti2003-cz, Ioannides2008-bs, Gaspar1998-gy, Cuberes2013-js, noauthor_2012-tg, Ciccone2006-uv, Charlot2004-zr, Cairns1997-nc, Arzaghi2008-ea, Bray2018-tx, Bartelme2017-in, Herrendorf2014-jx, Michaels2012-et, Behrens2017-mc, Cristea2015-ls, Acemoglu2007-uz, Hansen2002-ij, Aarland2007-dh, Rossi-Hansberg2007-tm

### 2020-07-31 text/manuscript.tex
Move regression into main tex file

@@
 {\bf Employment decline was sharpest in customer-facing industries.}}
-\input{regression.tex}
+
+{\setlength{\tabcolsep}{-2pt}
+{\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}\begin{tabular}{l*{4}{D{.}{.}{-1}}}\hline\hline
+                    &\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}\\
+                    &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} \\
+\hline
+Customer-facing~workers (share, [0,1])&      -0.418\sym{**} &      -0.463\sym{***}&       0.012         \\
+                    &     (0.164)         &     (0.152)         &     (0.173)         \\
+[1em]
+Teamwork-intensive~workers (share, [0,1])&       0.024         &       0.254         &       0.600         \\
+                    &     (0.563)         &     (0.532)         &     (0.839)         \\
+[1em]
+Presence-intensive~workers (share, [0,1])&       0.079         &      -0.051         &      -0.005         \\
+                    &     (0.125)         &     (0.136)         &     (0.113)         \\
+[1em]
+Change~in~number~of monthly visits (log)&                     &       0.185\sym{***}&      -0.119         \\
+                    &                     &     (0.063)         &     (0.131)         \\
+[1em]
+\hspace*{1em}$\times$~customer-facing~share ([0,1])&                     &                     &       1.021\sym{**} \\
+                    &                     &                     &     (0.447)         \\
+[1em]
+\hspace*{1em}$\times$~teamwork-intensive~share ([0,1])&                     &                     &       0.332         \\
+                    &                     &                     &     (1.500)         \\
+\hline
+Observations        &          79         &          78         &          78         \\
+\(R^{2}\)           &       0.187         &       0.302         &       0.435         \\
+\hline\hline
+\end{tabular}
+}
+
 \begin{flushleft} Regression results of change in log industry employment between February and May 2020 estimated by ordinary least squares (unweighted).

### 2020-09-03 text/manuscript.tex
Correct numbers to match replication package

@@
 Here we provide theory-based measures of the reliance of U.S. businesses on human interaction, detailed by industry and geographic location.
-We find that, before the pandemic hit, 35 million workers worked in occupations that rely heavily on face-to-face communication or require close physical proximity to other workers.
+We find that, before the pandemic hit, 43 million workers worked in occupations that rely heavily on face-to-face communication or require close physical proximity to other workers.
 Many of these workers lost their jobs since.
@@
 ...&&\\
-Mining          &2.0    &660\\
 Wholesale Trade	&1.8	&5,934\\
@@
 Manufacturing	&1.1	&12,852\\
+Management of Companies and Enterprises	&1.1	&2,447\\
 Agriculture, Forestry, Fishing and Hunting	&0.5	&55\\

### 2020-09-03 text/manuscript.tex
Add Zenodo DOI
Fix typos

@@
 \\
-\textbf{2} KRTK KTI, Budapest, Hungary
+\textbf{2} Centre for Economic and Regional Studies, Budapest, Hungary
 \\
-\textbf{3} CEPR, London, UK
+\textbf{3} CEPR, London, United Kingdom
 \\
@@
 \section*{Data Availability Statement}
-The mobility data used in thirds paper \cite{SafeGraph2020-gn} is proprietary, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium.
+The mobility data used in this paper \cite{SafeGraph2020-gn} is proprietary, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium.
 The authors are not affiliated with this consortium.
@@
 
-The code and all other data underlying our analysis are licensed for public use and will be made available on Zenodo.
+The code and all other data underlying our analysis are licensed for public use and are available on Zenodo at \url{http://doi.org/10.5281/zenodo.4013502}.
 

### 2020-09-03 text/manuscript.tex
Remove S2, S3, update Zenodo link

@@
 
-The code and all other data underlying our analysis are licensed for public use and are available on Zenodo at \url{http://doi.org/10.5281/zenodo.4013502}.
+The code and all other data underlying our analysis are licensed for public use and are available on Zenodo at \url{http://doi.org/10.5281/zenodo.4013863}.
 
@@
 {\bf Social distancing exposure by sector.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the industry.
-``Communication share'' refers to the share of workers who are either teamwork-intensive or customer-facing.
-``Affected share'' refers to the share of workers in any of the three occupation groups.
-Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v2.0/data/derived/industry-index.csv}.
-
-\paragraph*{S2 Full table of ZIP-codes.}
-\label{S2_File}
-{\bf Social distancing exposure by location.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the ZIP code.
-``Communication share'' refers to the share of workers who are either teamwork-intensive or customer-facing.
-``Affected share'' refers to the share of workers in any of the three occupation groups.
-Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v2.0/data/derived/location-index.csv}.
-
-\paragraph*{S3 Data repository.}
-\label{S3_URL}
-{\bf Replication code and data.} Replication code and data are available at \url{https://github.com/ceumicrodata/social-distancing/tree/v2.0}.
+``communication\_share'' refers to the share of workers who are either teamwork-intensive or customer-facing.
+``affected\_share'' refers to the share of workers in any of the three occupation groups.
 

### 2020-09-03 text/manuscript.tex
Include .bbl in .tex

@@
 
-%\begin{thebibliography}{10}
+\begin{thebibliography}{10}
 
-%\end{thebibliography}
+\bibitem{Bootsma2007-ww}
+Bootsma MCJ, Ferguson NM.
+\newblock The effect of public health measures on the 1918 influenza pandemic
+  in {US} cities.
+\newblock Proc Natl Acad Sci. 2007;.
 
-\bibliography{socdist}
+\bibitem{Markel2007-ad}
+Markel H, Lipman HB, Navarro JA, Sloan A, Michalsen JR, Stern AM, et~al.
+\newblock Nonpharmaceutical interventions implemented by {US} cities during the
+  1918-1919 influenza pandemic.
+\newblock JAMA. 2007;298(6):644--654.
+
+\bibitem{Hatchett2007-gc}
+Hatchett RJ, Mecher CE, Lipsitch M.
+\newblock Public health interventions and epidemic intensity during the 1918
+  influenza pandemic.
+\newblock Proc Natl Acad Sci. 2007;104(18):7582--7587.
+
+\bibitem{Wilder-Smith2020-jj}
+Wilder-Smith A, Freedman DO.
+\newblock Isolation, quarantine, social distancing and community containment:
+  pivotal role for old-style public health measures in the novel coronavirus
+  ({2019-nCoV}) outbreak.
+\newblock J Travel Med. 2020;27(2).
+
+\bibitem{Anderson2020-qk}
+Anderson RM, Heesterbeek H, Klinkenberg D, Hollingsworth TD.
+\newblock How will country-based mitigation measures influence the course of
+  the {COVID-19} epidemic?
+\newblock Lancet. 2020;.
+
+\bibitem{Cohen2020-jw}
+Cohen J, Kupferschmidt K.
+\newblock Mass testing, school closings, lockdowns: Countries pick tactics in
+  `war' against coronavirus.
+\newblock Science. 2020;.
+
+\bibitem{Thompson2020-lc}
+Thompson SA, Serkez Y.
+\newblock How Has Your State Reacted to Social Distancing?
+\newblock The New York Times. 2020;.
+
+\bibitem{noauthor_2020-xi}
+Mayor de Blasio Issues New Guidance to New Yorkers; 2020.
+\newblock
+  \url{https://www1.nyc.gov/office-of-the-mayor/news/173-20/mayor-de-blasio-issues-new-guidance-new-yorkers}.
+
+\bibitem{Adda2016-mn}
+Adda J.
+\newblock Economic Activity and the Spread of Viral Diseases: Evidence from
+  High Frequency Data.
+\newblock Q J Econ. 2016;131(2):891--941.
+
+\bibitem{Wren-Lewis2020-vc}
+Wren-Lewis S.
+\newblock The economic effects of a pandemic.
+\newblock In: Baldwin R, Weder~di Mauro B, editors. Economics in the Time of
+  {COVID-19}. London, UK: CEPR Press; 2020. p. 109--112.
+
+\bibitem{Henderson2010-mv}
+Henderson JV.
+\newblock Cities and Development.
+\newblock J Reg Sci. 2010;50(1):515--540.
+
+\bibitem{Henderson2002-ji}
+Henderson V.
+\newblock Urbanization in Developing Countries.
+\newblock World Bank Res Obs. 2002;17(1):89--112.
+
+\bibitem{Herrendorf2014-jx}
+Herrendorf B, Rogerson R, Valentinyi {\'A}.
+\newblock Growth and Structural Transformation.
+\newblock In: Aghion P, Durlauf SN, editors. Handbook of Economic Growth.
+  vol.~2. Elsevier; 2014. p. 855--941.
+
+\bibitem{Duarte2019-kc}
+Duarte M, Restuccia D.
+\newblock Relative Prices and Sectoral Productivity.
+\newblock J Eur Econ Assoc. 2019;.
+
+\bibitem{Dingel2020-lh}
+Dingel J, Neiman B.
+\newblock How Many Jobs Can be Done at Home?
+\newblock Becker Friedman Institute, University of Chicago; 2020.
+
+\bibitem{von2020labour}
+Von~Gaudecker HM, Holler R, Janys L, Siflinger B, Zimpelmann C.
+\newblock Labour supply in the early stages of the CoViD-19 Pandemic: Empirical
+  Evidence on hours, home office, and expectations. 2020;.
+
+\bibitem{Charlot2004-zr}
+Charlot S, Duranton G.
+\newblock Communication externalities in cities.
+\newblock J Urban Econ. 2004;56(3):581--613.
+
+\bibitem{Tian2019-wq}
+Tian L.
+\newblock Division of Labor and Productivity Advantage of Cities: Theory and
+  Evidence from Brazil; 2019.
+
+\bibitem{National_Center_for_ONET_Development2020-wj}
+{National Center for O*NET Development}. {O*NET} {OnLine} [dataset]; 2020.
+
+\bibitem{CBP}
+{U S  Bureau of the Census}. County Business Patterns [dataset]; 2017.
+
+\bibitem{SafeGraph2020-gn}
+{SafeGraph}. Patterns [dataset]; 2020.
+
+\bibitem{ATUS}
+{U S  Bureau of Labor Statistics}. American Time Use Survey [dataset]; 2018.
+
+\bibitem{Smith1778-qq}
+Smith A.
+\newblock An Inquiry into the Nature and Causes of the Wealth of Nations (Book
+  I).
+\newblock London: W. Strahan; T. Cadell; 1778.
+
+\bibitem{Becker1992-ac}
+Becker GS, Murphy KM.
+\newblock The Division of Labor, Coordination Costs, and Knowledge.
+\newblock Q J Econ. 1992;107(4):1137--1160.
+
+\bibitem{Marshall1920-ps}
+Marshall A.
+\newblock Principles of Economics (eighth edition).
+\newblock London: MacMillan; 1920.
+
+\bibitem{Krugman1991-gr}
+Krugman P.
+\newblock Geography and Trade.
+\newblock Cambridge: MIT Press; 1991.
+
+\bibitem{Garicano2009-jv}
+Garicano L, Hubbard TN.
+\newblock Specialization, Firms, and Markets: The Division of Labor within and
+  between Law Firms.
+\newblock J Law Econ Organ. 2009;25(2):339--371.
+
+\bibitem{Firpo2011-hp}
+Firpo S, Fortin NM, Lemieux T.
+\newblock Occupational Tasks and Changes in the Wage Structure.
+\newblock IZA; 2011. 5542.
+
+\bibitem{Autor2013-sh}
+Autor DH, Dorn D.
+\newblock The Growth of {Low-Skill} Service Jobs and the Polarization of the
+  {US} Labor Market.
+\newblock Am Econ Rev. 2013;103(5):1553--1597.
+
+\bibitem{Jin2020-tq}
+Jin B, McGill A. Who is most at risk in the coronavirus crisis: 24 million of
+  the lowest-income workers; 2020.
+\newblock
+  \url{https://www.politico.com/interactives/2020/coronavirus-impact-on-low-income-jobs-by-occupation-chart/}.
+
+\bibitem{Leibovici2020-qr}
+Leibovici F, Santacreu AM, Famiglietti M. Social Distancing and
+  {Contact-Intensive} Occupations; 2020.
+\newblock
+  \url{https://www.stlouisfed.org/on-the-economy/2020/march/social-distancing-contact-intensive-occupations}.
+
+\bibitem{Mongey2020-qc}
+Mongey S, Weinberg A.
+\newblock Characteristics of workers in low work-from-home and high
+  personal-proximity occupations; 2020.
+
+\bibitem{CES}
+{U S  Bureau of Labor Statistics}. Current Employment Statistics [dataset];
+  2020.
+
+\bibitem{employment-matrix}
+{U S  Bureau of Labor Statistics}. National Employment Matrix [dataset]; 2020.
+
+\bibitem{Caliendo2014-mr}
+Caliendo L, Parro F, Rossi-Hansberg E, Sarte PD.
+\newblock The Impact of Regional and Sectoral Productivity Changes on the
+  {U.S}. Economy.
+\newblock National Bureau of Economic Research, Inc; 2014. 20168.
+
+\bibitem{Caselli2020-nf}
+Caselli F, Koren M, Lisicky M, Tenreyro S.
+\newblock Diversification Through Trade.
+\newblock Q J Econ. 2020;135(1):449--502.
+
+\bibitem{Baldwin2020-wb}
+Baldwin R, Tomiura E.
+\newblock Thinking ahead about the trade impact of {COVID-19}.
+\newblock In: Baldwin R, Weder~di Mauro B, editors. Economics in the Time of
+  {COVID-19}. London, UK: CEPR Press; 2020. p. 59--61.
+
+\bibitem{Barrot2020-jf}
+Barrot JN, Grassi B, Sauvagnat J.
+\newblock Sectoral effects of social distancing; 2020.
+
+\bibitem{Gaspar1998-gy}
+Gaspar J, Glaeser E.
+\newblock Information Technology and the Future of Cities.
+\newblock J Urban Econ. 1998;43(1):136--156.
+
+\bibitem{Storper2004-mg}
+Storper M, Venables AJ.
+\newblock Buzz: face-to-face contact and the urban economy.
+\newblock J Econ Geogr. 2004;4(4):351--370.
+
+\bibitem{Cuberes2013-js}
+Cuberes D.
+\newblock Are Internet and {Face-to-Face} Contacts Complements or Substitutes?
+  Evidence from Internet Traffic between Cities; 2013. 2013010.
+
+\bibitem{Glaeser2002-mw}
+Glaeser EL, Shapiro JM.
+\newblock Cities and Warfare: The Impact of Terrorism on Urban Form.
+\newblock J Urban Econ. 2002;51(2):205--224.
+
+\bibitem{Harrigan2002-ik}
+Harrigan J, Martin P.
+\newblock Terrorism and the Resilience of Cities.
+\newblock Economic Policy Review. 2002;8(2).
+
+\end{thebibliography}
 

### 2020-09-05 text/manuscript.tex
Fix suggestions of Gergely. This is consistent with 10.5281/zenodo.4016325

@@
 Wholesale Trade						&8	&12	&15	&12\\
-Transportation and Warehousing 		&8	&8	&14	&33\\
+Transportation and Warehousing 		&8	&8	&14	&32\\
 Prof., Scient., and Technical Serv.	&5	&10	&12	&1\\
@@
 Accommodation and Food Services	&26.1	&14,394\\
-Educational Services	&22.2	&3,8328\\
+Educational Services	&22.2	&3,828\\
 Other Services (except Public Admin.)	&14.5	&5,941\\
